### 2021-04-18 Paper.tex
Initial Overleaf Import

% Version 2020-01-06
% update – 161114 by Ken Arroyo Ohori: made spacing closer to Word template throughout, put proper quotes everywhere, removed spacing that could cause labels to be wrong, added non-breaking and inter-sentence spacing where applicable, removed explicit newlines
% update – 010819 by Dennis Wittich: made spacing and font size closer to Word template, updated references and refernces style
% update – 042319 by Dennis Wittich: font size of captions set to 'small', first author names are shortened, hyphenation fixed
% update – 010620 by Dennis Wittich: Footnotes alignment set to left

\documentclass{isprs} % isprs class modified 23-04-2019 (Dennis Wittich)
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{geometry} % added 27-02-2014 Markus Englich
\usepackage{epstopdf}
\usepackage{natbib}
\usepackage[colorlinks, allcolors=blue]{hyperref}
%\bibliographystyle{apalike}
\usepackage[labelsep=period]{caption}  % added 14-04-2016 Markus Englich - Recommendation by Sebastian Brocks
\usepackage[british]{babel} 
\usepackage[hang]{footmisc}
\def\footnotemargin{1em} % added 08-01-2020 Dennis Wittich
\usepackage{fancyref}

%\usepackage[authoryear]{natbib}
%\def\bibhang{0pt}

\geometry{a4paper, top=25mm, left=20mm, right=20mm, bottom=25mm, headsep=10mm, footskip=12mm} % added 27-02-2014 Markus Englich
%\usepackage{enumitem}

%\usepackage{isprs}
%\usepackage[perpage,para,symbol*]{footmisc}

%\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\captionsetup{justification=centering,font=normal} % thanks to Niclas Borlin 05-05-2016
\captionsetup[figure]{font=small} % added 23-04-2019 Dennis Wittich
\captionsetup[table]{font=small} % added 23-04-2019 Dennis Wittich

% Location of the images
\graphicspath{{figures/}}

\begin{document}

\title{Assessing Digital Elevation Models with different image overlap using photogrammetry}

% KAO: Remove extra spacing
\author{Robert van de Vlasakker}

% KAO: Remove extra newline
\address{} % Not needed

% If the corresponding author is NOT the final author, always add a % space before the subsequent comma, i.e.
% first author name\textsuperscript{a,}\thanks{Corresponding author} , % second author name \textsuperscript{b}, etc.
% thanks to Niclas Borlin 05-05-2016

% BB: leave these empty, but do not delete
\commission{}{} %This field is optional.
\workinggroup{} %This field is optional.
\icwg{}   %This field is optional.

% KAO: Use times symbol
\abstract{
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
}

\keywords{Photogrammetry, Digital Elevation Model, Image Overlap}

\maketitle

%\saythanks % added 28-02-2014 Markus Englich

\section{Introduction}\label{Introduction}

Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
The process uses similar points visible on multiple images to determine the points in space.
The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
When a point is visible on more images, the reconstruction certainty we be higher.
This is especially the case with the reconstruction of irregular formed object like vegetation \citep{AccessingImageOverlap}.
With irregular objects, a higher overlap is preferred to capture each side of the object.
If parts of the object are not visible on the image, they will not be reconstructed in the point cloud.
So the overlap strongly influences the point cloud density in the dense cloud \citep{OptimalAltOverWeath}.
In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
However, a higher image overlap, does not automatically results in a higher point accuracy (x,y,z) \citep{EffectofUABimgcamover}.
By investigating how reducing the image overlap influences photogrammetry results, time and computing power may be saved without loosing too much spatial information.

With the development of cheap Unmanned Aerial Vehicles (UAV) photogrammetry has become more and more popular. 
UAV's come with high resolution cameras, GNSS and are available almost anywhere these days.
While UAV's do come with high resolution sensors and relatively cheap, small, high capacity batteries are not available \citep{UAVpopularity}.
A high image overlap takes longer to gather than a low image overlap. 
A drone can use a higher altitude so the sensor captures a larger area.
however, with a higher flight altitude the detail of the image will be less than that of a drone with a lower flight altitude.
This way the gathering process takes longer, and the UAV might even need to switch batteries instead of taking the images in a single flight.

\section{Materials and Methods}

\subsection{Study Area}\label{sec:Study Area}
The data covers an area in Ghana, about 20km south east of Ejura (lat. 7.3064212, lon. -1.164493). 
The area of interest is about 25000 m\textsuperscript{2}. 
The area consists mostly of sanvannah.
There are a few trees present.
\begin{figure}[htp]
    \centering
    \includegraphics[width=4cm]{locationwide.png}
    \includegraphics[width=4cm]{locationzoom.png}
    \caption{Area of Interest and Image Locations}
    \label{fig:areaofinterest}
\end{figure}
Each image has a resolution of 4000 times 3000 and was taken by a DJI Phantom 3.
The images all contain GNNS location (WGS84). 
Their exact location can be found in figure \ref{fig:areaofinterest}.

\subsection{Image Selection and Processing}
For image processing and DEM generation Agisoft Metashape Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used.
First, the complete data set has been aligned on medium quality.
Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.

The generation of three-dimensional (3D) dense point clouds from the images were performed for each acquisition using the proprietary software Agisoft Photoscan Professional version 1.1 (Agisoft LLC., St. Petersburg, Russia)

\subsection{DEM}

% KAO: Sloppy spacing ensures non-overfull lines. Can be removed if this is not an issue.
\sloppy

{
	\begin{spacing}{1.17}
		\normalsize
		\bibliography{bibliography} % Include your own bibliography (*.bib), style is given in isprs.cls
	\end{spacing}
}

\vspace{1cm}
\end{document}

### 2021-04-18 Proposal.tex
Initial Overleaf Import

--- 2021-04-18 Paper.tex
@@
-% Version 2020-01-06
-% update – 161114 by Ken Arroyo Ohori: made spacing closer to Word template throughout, put proper quotes everywhere, removed spacing that could cause labels to be wrong, added non-breaking and inter-sentence spacing where applicable, removed explicit newlines
-% update – 010819 by Dennis Wittich: made spacing and font size closer to Word template, updated references and refernces style
-% update – 042319 by Dennis Wittich: font size of captions set to 'small', first author names are shortened, hyphenation fixed
-% update – 010620 by Dennis Wittich: Footnotes alignment set to left
-
-\documentclass{isprs} % isprs class modified 23-04-2019 (Dennis Wittich)
-\usepackage{subfigure}
-\usepackage{setspace}
-\usepackage{geometry} % added 27-02-2014 Markus Englich
-\usepackage{epstopdf}
+\documentclass{article}
+\usepackage[utf8]{inputenc}
 \usepackage{natbib}
 \usepackage[colorlinks, allcolors=blue]{hyperref}
-%\bibliographystyle{apalike}
-\usepackage[labelsep=period]{caption}  % added 14-04-2016 Markus Englich - Recommendation by Sebastian Brocks
-\usepackage[british]{babel} 
-\usepackage[hang]{footmisc}
-\def\footnotemargin{1em} % added 08-01-2020 Dennis Wittich
-\usepackage{fancyref}
-
-%\usepackage[authoryear]{natbib}
-%\def\bibhang{0pt}
-
-\geometry{a4paper, top=25mm, left=20mm, right=20mm, bottom=25mm, headsep=10mm, footskip=12mm} % added 27-02-2014 Markus Englich
-%\usepackage{enumitem}
-
-%\usepackage{isprs}
-%\usepackage[perpage,para,symbol*]{footmisc}
-
-%\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
-\captionsetup{justification=centering,font=normal} % thanks to Niclas Borlin 05-05-2016
-\captionsetup[figure]{font=small} % added 23-04-2019 Dennis Wittich
-\captionsetup[table]{font=small} % added 23-04-2019 Dennis Wittich
-
-% Location of the images
-\graphicspath{{figures/}}
+\bibliographystyle{apalike}
+\title{Accessing Digital Elevation Models with different image overlap using photogrammetry}
+\author{Robert Vlasakker, van de}
+\date{April 2021}
 
@@
 
-\title{Assessing Digital Elevation Models with different image overlap using photogrammetry}
-
-% KAO: Remove extra spacing
-\author{Robert van de Vlasakker}
-
-% KAO: Remove extra newline
-\address{} % Not needed
-
-% If the corresponding author is NOT the final author, always add a % space before the subsequent comma, i.e.
-% first author name\textsuperscript{a,}\thanks{Corresponding author} , % second author name \textsuperscript{b}, etc.
-% thanks to Niclas Borlin 05-05-2016
-
-% BB: leave these empty, but do not delete
-\commission{}{} %This field is optional.
-\workinggroup{} %This field is optional.
-\icwg{}   %This field is optional.
-
-% KAO: Use times symbol
-\abstract{
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-}
-
-\keywords{Photogrammetry, Digital Elevation Model, Image Overlap}
-
 \maketitle
 
-%\saythanks % added 28-02-2014 Markus Englich
-
-\section{Introduction}\label{Introduction}
-
+\section{Introduction}
+With the development of cheap Unmanned Aerial Vehicles (UAV) photogrammetry has become more and more popular. 
+UAV's come with high resolution cameras, GNSS and are available almost anywhere these days.
 Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
 The process uses similar points visible on multiple images to determine the points in space.
-The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
+So the reconstruction process is strongly dependent on the overlap between different images. 
 When a point is visible on more images, the reconstruction certainty we be higher.
@@
 So the overlap strongly influences the point cloud density in the dense cloud \citep{OptimalAltOverWeath}.
-In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
-However, a higher image overlap, does not automatically results in a higher point accuracy (x,y,z) \citep{EffectofUABimgcamover}.
-By investigating how reducing the image overlap influences photogrammetry results, time and computing power may be saved without loosing too much spatial information.
 
-With the development of cheap Unmanned Aerial Vehicles (UAV) photogrammetry has become more and more popular. 
-UAV's come with high resolution cameras, GNSS and are available almost anywhere these days.
+\section{Problem Statement}
 While UAV's do come with high resolution sensors and relatively cheap, small, high capacity batteries are not available \citep{UAVpopularity}.
@@
 This way the gathering process takes longer, and the UAV might even need to switch batteries instead of taking the images in a single flight.
+In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
+However, a higher image overlap, does not automatically results in a higher point accuracy (x,y,z) \citep{EffectofUABimgcamover}.
+By investigating how reducing the image overlap influences photogrammetry results, time and computing power may be saved without loosing too much spatial information.
+% Needed to set 3. at new page
 
-\section{Materials and Methods}
+\section{Research Questions}
 
-\subsection{Study Area}\label{sec:Study Area}
-The data covers an area in Ghana, about 20km south east of Ejura (lat. 7.3064212, lon. -1.164493). 
-The area of interest is about 25000 m\textsuperscript{2}. 
-The area consists mostly of sanvannah.
-There are a few trees present.
-\begin{figure}[htp]
-    \centering
-    \includegraphics[width=4cm]{locationwide.png}
-    \includegraphics[width=4cm]{locationzoom.png}
-    \caption{Area of Interest and Image Locations}
-    \label{fig:areaofinterest}
-\end{figure}
-Each image has a resolution of 4000 times 3000 and was taken by a DJI Phantom 3.
-The images all contain GNNS location (WGS84). 
-Their exact location can be found in figure \ref{fig:areaofinterest}.
+\emph{How is the result of the Digital Elevation Model influenced by reducing the image overlap by using the Metashape 'Reduce Overlap' function?}
 
-\subsection{Image Selection and Processing}
-For image processing and DEM generation Agisoft Metashape Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used.
-First, the complete data set has been aligned on medium quality.
-Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.
+\section{Methods}
+For this research a data set from the Advanced Earth Observation will be used, the 'Koyage' data set along with Agisoft Metashape (1.6.5.)
+This data set contains 111 images with a resolution of 4000 x 3000, the images all contain WGS84 coordinates with the image location. 
+The images will first be aligned to generate a dense cloud (medium quality, no depth filtering).
+Next, a mesh will be created, this is needed for Metashape to calculate the images that can be left out.
+For the mesh the dense cloud will be used as source and the mesh will be a height field (2.5).
+A high face count (653.852 faces) will be used.
 
-The generation of three-dimensional (3D) dense point clouds from the images were performed for each acquisition using the proprietary software Agisoft Photoscan Professional version 1.1 (Agisoft LLC., St.
-Petersburg, Russia)
+The 'Reduce Overlap' function will be used on all three settings (low, medium and high) to reduce the amount of images. 
+The dense cloud with be built again with the images selecting by the 'Reduce Overlap' function.
+The dense cloud will again be build at medium setting and no depth filtering
+Next a Digital Elevation Model (DEM) will be built using the Metashape software.
+For the DEM the dense cloud will be used as source data and interpolation will be used in case the point cloud contains bad/missing data.
+This process will be repeated three times with 'Reduce Overlap' on low, medium and high settings.
+Finally the different DEM's will be visually inspected and compared (e.g. using the difference). 
+The research will take place in the two last weeks of April 2021.
 
-\subsection{DEM}
-
-% KAO: Sloppy spacing ensures non-overfull lines. Can be removed if this is not an issue.
-\sloppy
-
-{
-	\begin{spacing}{1.17}
-		\normalsize
-		\bibliography{bibliography} % Include your own bibliography (*.bib), style is given in isprs.cls
-	\end{spacing}
-}
-
-\vspace{1cm}
+\bibliography{bibliography}
 \end{document}

### 2021-04-18 ISPRSguidelines_authors.tex
M&M edit

% Version 2020-01-06
% update – 161114 by Ken Arroyo Ohori: made spacing closer to Word template throughout, put proper quotes everywhere, removed spacing that could cause labels to be wrong, added non-breaking and inter-sentence spacing where applicable, removed explicit newlines
% update – 010819 by Dennis Wittich: made spacing and font size closer to Word template, updated references and refernces style
% update – 042319 by Dennis Wittich: font size of captions set to 'small', first author names are shortened, hyphenation fixed
% update – 010620 by Dennis Wittich: Footnotes alignment set to left

\documentclass{isprs} % isprs class modified 23-04-2019 (Dennis Wittich)
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{geometry} % added 27-02-2014 Markus Englich
\usepackage{epstopdf}
\usepackage[labelsep=period]{caption}  % added 14-04-2016 Markus Englich - Recommendation by Sebastian Brocks
\usepackage[british]{babel} 
\usepackage[hang]{footmisc}
\def\footnotemargin{1em} % added 08-01-2020 Dennis Wittich
\usepackage{fancyref}

%\usepackage[authoryear]{natbib}
%\def\bibhang{0pt}

\geometry{a4paper, top=25mm, left=20mm, right=20mm, bottom=25mm, headsep=10mm, footskip=12mm} % added 27-02-2014 Markus Englich
%\usepackage{enumitem}

%\usepackage{isprs}
%\usepackage[perpage,para,symbol*]{footmisc}

%\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\captionsetup{justification=centering,font=normal} % thanks to Niclas Borlin 05-05-2016
\captionsetup[figure]{font=small} % added 23-04-2019 Dennis Wittich
\captionsetup[table]{font=small} % added 23-04-2019 Dennis Wittich

\begin{document}

\title{GUIDELINES FOR AUTHORS PREPARING MANUSCRIPTS FOR PUBLICATION IN THE ISPRS ARCHIVES AND THE ISPRS ANNALS; adapted for GRS-32306 Advanced Earth Observation}

% KAO: Remove extra spacing
\author{
 M. O. Altan\textsuperscript{1}, G. Toz\textsuperscript{1}, I. Dowman\textsuperscript{2}, S. Kulur\textsuperscript{1}, D. Z. Seker\textsuperscript{1}, P. L\"owe\textsuperscript{3}, C. Heipke\textsuperscript{4,}\thanks{Corresponding author}}

% KAO: Remove extra newline
\address{
	\textsuperscript{1 }ITU, Civil Engineering Faculty, 80626 Maslak Istanbul, Turkey - (oaltan, tozg, kulur, seker)@itu.edu.tr\\
	\textsuperscript{2 }Dept.\ of Geomatic Engineering, University College London, Gower Street, London, WC1E 6BT UK - idowman@ge.ucl.ac.uk\\
	\textsuperscript{3 }German Institute for Economic Research, Berlin, Germany - ploewe@diw.de\\
	\textsuperscript{4 }Institute of Photogrammetry and GeoInformation, Leibniz Universit\"at Hannover, Germany - heipke@ipi.uni-hannover.de
}

% If the corresponding author is NOT the final author, always add a % space before the subsequent comma, i.e.
% first author name\textsuperscript{a,}\thanks{Corresponding author} , % second author name \textsuperscript{b}, etc.
% thanks to Niclas Borlin 05-05-2016

% BB: leave these empty, but do not delete
\commission{}{} %This field is optional.
\workinggroup{} %This field is optional.
\icwg{}   %This field is optional.

% KAO: Use times symbol
\abstract{
These guidelines are provided for preparation of papers accepted for publication in the series of Volumes of The International Archives of the Photogrammetry, Remote Sensing and Spatial Information Sciences and of The ISPRS Annals of the Photogrammetry, Remote Sensing and Spatial Information Sciences from ISPRS Congresses and Symposia, and other ISPRS events. These guidelines are issued to ensure a uniform style throughout these two series. All papers that are accepted by the relevant scientific committee of an ISPRS event will be published provided they arrive by the due date and they correspond to these guidelines. Reproduction is made directly from author-prepared manuscripts, in electronic or hardcopy form, in A4 paper size 297 mm $\times$ 210 mm (11.69 $\times$ 8.27 inches). To assure timely and efficient production of the Archives and Annals with a consistent and easy to read format, authors must submit their manuscripts in strict conformance with these guidelines. The Society may omit any paper that does not conform to the specified requirements. \textbf{There will be no opportunity for corrections or improvements of poorly prepared originals}.  
}

\keywords{Manuscripts, Proceedings, ISPRS Archives, ISPRS Annals, Guidelines for Authors, Styleguide}

\maketitle

%\saythanks % added 28-02-2014 Markus Englich

\section{MANUSCRIPT}\label{MANUSCRIPT}

% KAO: Sloppy spacing ensures non-overfull lines. Can be removed if this is not an issue.
\sloppy

\subsection{General Instructions}\label{sec:General Instructions}

The maximum paper length is restricted to 5 pages. The paper should have the following structure:

%\itemize
\begin{enumerate}
\setlength\itemsep{0em}\setlength\parskip{0em}\setlength\topsep{0em}\setlength\partopsep{0em}\setlength\parsep{0em} 
\item{Title of the paper} 
\item{Authors and affiliation}
\item{Keywords (6--8 words)}
\item{Abstract (100--250 words)}
\item{Introduction}
\item{Main body}
\item{Conclusions}
\item{Acknowledgements (if applicable)}
\item{References}
\item{Appendix (if applicable)}
\end{enumerate}

% KAO: Use proper quotes
Full papers submitted for double-blind review to the Annals must not contain any information 
which makes it possible to identify the authors. In particular, names and affiliations must be 
removed from the manuscript submitted for review. Also sentences such as ``As we have shown in 
previous work (Author\_x, 20xx)'' are to be avoided. Instead use a formulation such 
as ``Author\_x (20xx) has shown \ldots''. Note that submissions which have not been 
appropriately anonymised may be subject to immediate rejection.

All final papers should be submitted in BrightSpace before the deadline agreed upon.

% In Section~\ref{MANUSCRIPT} we present related work
\newpage            
\subsection{Page Layout, Spacing and Margins}\label{sec:Page Layout, Spacing and Margins}

The paper must be compiled in one column for the Title and Abstract and in two columns for all subsequent text. 
All text should be single-spaced, unless otherwise stated. Left and right justified typing is preferred. See \Fref{tab:Margin_settings} for margin settings.

\subsection{Preparation in electronic form}\label{sec:Preparation in electronic form}

% KAO: Remove newline
To assist authors in preparing their papers, styleguides for preparing digital versions of papers are 
provided in Word and/or LaTeX.

\subsection{Length and Font}\label{sec:Length and Font}

All manuscripts, except Invited Papers are limited to approximately five (5) single-spaced 
pages (A4 size), including abstracts, figures, tables and references. The font type Times New Roman with a size of nine (9) points is to be used.

% KAO: Removed spacing before label: can cause references to be wrong
\begin{table}[h]
	\centering
	\caption{Margin settings for A4 size paper}
		\begin{tabular}{|l|c|c|}\hline
			Setting&\multicolumn{2}{c|}{A4 size paper}\\\hline
			  &mm&inches\\
			 Top&25&1.0\\
			 Bottom&25&1.0\\
			 Left&20&0.8\\
			 Right&20&0.8\\
			 Column Width&82&3.2\\
			 Column Spacing&6&0.25\\\hline
		\end{tabular}
\label{tab:Margin_settings}
\end{table}

\section{TITLE AND ABSTRACT BLOCK}\label{sec:TITLE AND ABSTRACT BLOCK}

\subsection{Title}\label{sec:Title}

The title should appear centered in bold capital letters, at the top of the 
first page of the paper with a size of twelve (12) points and single-spacing. 
After one blank line, type the author(s) name(s), affiliation and mailing address 
(including e-mail) in upper and lower case letters, centred under the title. In the 
case of multi-authorship, group them by firm or organization as shown in the title 
of these Guidelines.

\subsection{Key Words}\label{sec:Key Words}

% KAO: Use proper quotes and dash
Leave two lines blank, then type \textbf{``KEY WORDS:''}
in bold capital letters, followed by 5--8 key words. Note that ISPRS does not provide a set 
list of key words any longer. Therefore, include those key words which you would 
use to find a paper with content you are preparing.

\subsection{Abstract}\label{sec:Abstract}

% KAO: Use proper quotes and dash
Leave two blank lines under the key words. Type \textbf{``ABSTRACT:''}
flush left in bold Capitals followed by one blank line. Start now
with a concise Abstract (100--250 words) which presents briefly the
content and very importantly, the news and results of the paper in
words understandable also to non-specialists.

\section{MAIN BODY OF TEXT}\label{sec:MAIN BODY OF TEXT}

Type text single-spaced, \textbf{with} one blank line between paragraphs and 
following headings. Start paragraphs flush with left margin.

\subsection{Headings}\label{sec:Headings}

% KAO: Remove explicit newlines in this section
Major headings are to be centered, in bold capitals without 
underlining, after two blank lines and followed by a one blank line.

Type subheadings flush with the left margin in bold upper case and lower 
case letters. Subheadings are on a separate line between two single blank lines.

Subsubheadings are to be typed in bold upper case and lower case letters 
after one blank line flush with the left margin of the page, with text 
following on the same line. Subsubheadings may be followed by a period 
or colon, they may also be the first word of the paragraph's sentence.

Use decimal numbering for headings and subheadings.

\subsection{Footnotes}\label{sec:Footnotes}

Mark footnotes in the text with a number (1); use the same number for a 
second footnote of the paper and so on. Place footnotes at the bottom of 
the page, separated from the text above it by a horizontal line.

\subsection{Illustrations and Tables}\label{sec:Illustrations and Tables}

\subsubsection{Placement:}\label{sec:Placement}

Figures must be placed in the appropriate location in the document, 
as close as practicable to the reference of the figure in the text. 
While figures and tables are usually aligned horizontally on the page, 
large figures and tables sometimes need to be turned on their sides. 
If you must turn a figure or table sideways, please be sure that the 
top is always on the left-hand side of the page.

\subsubsection{Captions:}\label{sec:Captions}

All captions should be typed in upper and lower case letters, 
centered directly beneath the illustration and above a table. Use single spacing if they 
use more than one line. All captions are to be numbered consecutively, 
e.g. Figure 1, Figure 2, Figure 3, ..  and Table 1, Table 2, Table 3, ...

% KAO: Remove spacing before label: can cause reference to be wrong
\begin{figure}[ht!]
\begin{center}
		\includegraphics[width=1.0\columnwidth]{figures/test_sites/fig1.eps}
	\caption{Figure placement and numbering}
\label{fig:figure_placement}
\end{center}
\end{figure}

\subsubsection{Copyright:}\label{sec:Copyright}

% KAO: Inter-sentence spacing
If your article contains any copyrighted illustrations or imagery, 
please include a statement of copyright such as: \copyright~SPOT Image Copyright 20xx 
(fill in year), CNES\@. It is the author's responsibility to obtain any necessary 
copyright permission. After publication, your article is distributed under \underline{the Creative 
Commons Unported License} and you retain the copyright.

\subsection{Equations, Symbols and Units}\label{sec:Equations, Symbols and Units}

\subsubsection{Equations:}\label{sec:Equations}

Equations should be numbered consecutively throughout the paper. The equation 
number is enclosed in parentheses and placed flush right. Leave one blank line 
before and after equations:

\begin{equation}\label{equ:1}
	x = x_0 -c \frac{X - X_0}{Z - Z_0}; y = y_0 -c \frac{Y - Y_0}{Z - Z_0}
\end{equation}

\begin{tabbing} 
where \hspace{0.6cm} \= $c$ = focal length\\
\> $x,y$ = image coordinates\\
\> $X_0,Y_0, Z_0$ = coordinates of projection center\\
\> $X, Y, Z$ = object coordinates
\end{tabbing}

\subsubsection{Symbols and Units:}\label{sec:Symbols and Units}
Use the SI (Syst\`{e}me Internationale) Units and Symbols. Unusual characters 
or symbols should be explained in a list of nomenclature.

% KAO: Non-breaking space
\subsection{References}\label{sec:References}
References should be cited in the text, thus~\cite{smith1987rep}, and listed in alphabetical order in the reference section. The following arrangements should be used:

% KAO: Use proper quotes and non-breaking space
\subsubsection{References from Journals:} 
Journals should be cited like~\cite{smith1987} or~\cite{michalis2008}. Names of journals can be abbreviated according to the ``International List of Periodical Title Word Abbreviations''. In case of doubt, write names in full.

\subsubsection{References from Books:} 
Books should be cited like~\cite{foerstner2016}.

\subsubsection{References from other Literature:}
Other literature should be cited like~\cite{smith1987rep} and~\cite{smith2000}.

\subsubsection{References from Websites:}
References from the internet should be cited like~\cite{chan2017} and~\cite{maas2017}. Use of persistent identifiers such as the Digital Object Identifier (DOI) rather than URLs is strongly advised. In this case last date of visiting the website can be omitted, as the identifier will not change.

\subsubsection{References from Research Data:}
References from research data should be cited like~\cite{dubayah2013}.

\subsubsection{References from Software Projects:}
References to a software project as a high level container including multiple versions of the software should be cited like~\cite{grass2017}.

\subsubsection{References from Software Versions:}
References to a specific software version should be cited like~\cite{grass2015}.

\subsubsection{References from Software Project Add-ons:}
References to a specific software add-on to a software project should be cited like~\cite{lennert2017}.

\subsubsection{References from Software Repository:}
References from software repositories should be cited like~\cite{gago2016}.

\section*{ACKNOWLEDGEMENTS (Optional)}\label{ACKNOWLEDGEMENTS}
Acknowledgements of support for the project/paper/author are welcome.

{
	\begin{spacing}{1.17}
		\normalsize
		\bibliography{ISPRSguidelines_authors} % Include your own bibliography (*.bib), style is given in isprs.cls
	\end{spacing}
}

\section*{APPENDIX (Optional)}\label{APPENDIX}

Any additional supporting data may be appended, provided the paper does not exceed the limits given above.

\vspace{1cm}
\textit{Revised January 2020}

\end{document}

### 2021-04-18 Paper.tex
M&M edit

@@
 \usepackage{natbib}
+\usepackage{tabularx}
+\usepackage{booktabs}
 \usepackage[colorlinks, allcolors=blue]{hyperref}
@@
     \includegraphics[width=4cm]{locationwide.png}
-    \includegraphics[width=4cm]{locationzoom.png}
+    \includegraphics[width=4cm]{locationzoom2.png}
     \caption{Area of Interest and Image Locations}
@@
 The images all contain GNNS location (WGS84). 
+The complete data set consists of 111 images.
 Their exact location can be found in figure \ref{fig:areaofinterest}.
 
-\subsection{Image Selection and Processing}
-For image processing and DEM generation Agisoft Metashape Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used.
+\subsection{Image Processing}
+For image processing and DEM generation Agisoft Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used.
 First, the complete data set has been aligned on medium quality.
 Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.
+A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
+After the mesh the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry
 
-The generation of three-dimensional (3D) dense point clouds from the images were performed for each acquisition using the proprietary software Agisoft Photoscan Professional version 1.1 (Agisoft LLC., St.
-Petersburg, Russia)
+\textbf{Reduce Overlap.} 
+The algorithm of the Reduce Overlap function tries to select a minimal amount of images such that each point of the model is observed from N locations/angles.
+If a point is observed multiple times from the same location/angle, than this still counts as one. 
+The exact algorithm and parameters behind the Agisoft Reduce Overlap function are unknown.
+In Agisoft Metashape the 'Reduce Overlap' had three different settings, low, medium and high.
+
+After the amount of images have been reduced, the data have been processed on medium for the image alignment and on medium without depth filtering for the dense cloud creation.
+In table \ref{tab:ImageProcessing} an overview of the image processing results can be found.
+
+\begin{table}[htb]
+    \centering
+    \caption{Image Processing Results}
+    \begin{tabular}{@{}cccc@{}}
+    \toprule
+    \textbf{Setting} & \textbf{Images} & \multicolumn{1}{l}{\textbf{Sparse Cloud}} & \multicolumn{1}{l}{\textbf{Dense Cloud}} \\ \midrule
+    -      & 111 & 80,901 & 3,269,264 \\
+    Low    & 44  & 37,886 & 4,172,783 \\
+    Medium & 70  & 54,556 & 3,313,399 \\
+    High   & 75  & 49,692 & 3,276,832 \\ \bottomrule
+    \label{tab:ImageProcessing}
+\end{tabular}
+\end{table}
 
 \subsection{DEM}
+The source data for the DEM's are the dense cloud results. 
+The TIN algorithm is used to built the DEM's \citep{axelsson1999processing}.
 

### 2021-04-18 Paper.tex
wrap up 0418 added all sections

@@
 The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
-When a point is visible on more images, the reconstruction certainty we be higher.
+When a point is visible on more images, the reconstruction certainty will be higher.
 This is especially the case with the reconstruction of irregular formed object like vegetation \citep{AccessingImageOverlap}.
@@
 A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
-After the mesh the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry
+After the mesh the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
+The mesh was set to create a 2.5D height field.
 
@@
 
+\section{Results}
+\section{Discussion}
+The amount of images used in the processing does not seem to influence the density of the dense cloud, which was also concluded by \citet{EffectofUABimgcamover}. 
+The input mesh for the Reduce Overlap was a 2.5D height field. 
+With more complex objects that need to processed as a real 3D object the amount of dense cloud may decrease if the amount of images is reduces significantly.
+An other option is that the Reduce Overlap function will not have much influence on the image count.
+
+\section{Conclusion}
+
 % KAO: Sloppy spacing ensures non-overfull lines. Can be removed if this is not an issue.

### 2021-04-21 Paper.tex
backup

@@
 \abstract{
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Photogrammetry is easy to use these days and can be used to create a digital elevation model of an area. 
+Image overlap plays an important role in the process of photogrammetry.
+A high overlap takes more time to gather in the field and takes longer to process.
+Less overlap usually results in a less accurate calculations. 
+In this paper the overlap of an area is artificially reduced and digital elevation models have been created with different image overlaps.
+The digital elevation models are compared to see how reducing the image overlap influences the result.
 }
 
-\keywords{Photogrammetry, Digital Elevation Model, Image Overlap}
+\keywords{Photogrammetry, Digital Elevation Model, Image Overlap, Agisoft Metashape}
 
@@
 However, a higher image overlap, does not automatically results in a higher point accuracy (x,y,z) \citep{EffectofUABimgcamover}. 
-By investigating how reducing the image overlap influences photogrammetry results, time and computing power may be saved without loosing too much spatial information.
-
-With the development of cheap Unmanned Aerial Vehicles (UAV) photogrammetry has become more and more popular. 
+With the development of cheap Unmanned Aerial Vehicles (UAV) photogrammetry has become more and more popular \citet{UAVAreMoreUsed}. 
 UAV's come with high resolution cameras, GNSS and are available almost anywhere these days.
@@
 This way the gathering process takes longer, and the UAV might even need to switch batteries instead of taking the images in a single flight.
+By reducing the image overlap, time and computing power may be saved without loosing too much spatial information.
+This main goal of this study is to investigate how different image overlap influence the DEM result that is created with photogrammetry.
 
@@
     \includegraphics[width=4cm]{locationwide.png}
-    \includegraphics[width=4cm]{locationzoom2.png}
-    \caption{Area of Interest and Image Locations}
+    \includegraphics[width=4cm]{imgloc.png}
+    \caption{Area of Interest and Unprocessed Image GPS Locations}
     \label{fig:areaofinterest}
@@
 \subsection{Image Processing}
-For image processing and DEM generation Agisoft Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used.
+For image processing and DEM generation Agisoft Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used \citep{AgisoftMetashape}.
 First, the complete data set has been aligned on medium quality.
@@
 The exact algorithm and parameters behind the Agisoft Reduce Overlap function are unknown.
+The input dataset was a 2.D height field mesh. 
+Because in this paper the comparison will be made with a DEM, a height field was computed.
 In Agisoft Metashape the 'Reduce Overlap' had three different settings, low, medium and high. 
+All of the settings are used to compute the images for further processing.
+
+\textbf{Camera Location.}
+In figure \ref{fig:cameralocation} the estimated camera locations can be found.
+The camera selection is done by the Reduce Overlap algorithm from Agisoft Metashape.
+The estimated camera location is done in the image processing.
+The images are matched based on an adapted version of the SIFT algorithm \citep{lowe1999object, AgisoftMetashape}.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=4cm]{loc_low.png}
+    \includegraphics[width=4cm]{loc_med.png}
+    \includegraphics[width=4cm]{loc_full.png}
+    \includegraphics[width=4cm]{loc_high.png}
+    \caption{Estimated camera location. 
+    White: used in the image processing, red: disabled in the image processing.\\
+    Clockwise: low, medium, high and full settings}
+    \label{fig:cameralocation}
+\end{figure}
 
@@
 The source data for the DEM's are the dense cloud results. 
+The Dense Cloud contains about the same amount of points with the exception for the lowest Reduce Overlap setting.
+This setting has resulted in the dense cloud with the most points.
 The TIN algorithm is used to built the DEM's \citep{axelsson1999processing}.
+The image overlap is now changed, therefore the DEM's have a slightly different extent.
+Because of this the largest common extent of the DEM's will be used to crop the DEM's resulting in four DEM's with an equal extent.
+The DEM's will also be scaled to check the differences between the DEM's without looking at the absolute values.
+The scaling will be done by subtracting the mean and dividing by the standard deviation.
 
 \section{Results}
+In figure \ref{fig:DemPlot_unscaled} are visualized using the same color range. 
+In this figure the DEM's do no look similar at all.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=8cm]{DemPlots.png}
+    \caption{DEM Results of the Reduce Overlap}
+    \label{fig:DemPlot_unscaled}
+\end{figure}
+
+As can be seen from figure \ref{fig:BoxPlot_unscaled} the DEM's are indeed different from each other. 
+The outliers in the boxplot figure are probably the vegetation that is present in the area.
+For the low setting the DEM values range from -19.4 to 19.0, for the medium setting the values range from -22.7 to 16.2, for the high setting the values range from 13.1 to 20.0 and for the full model from -4.8 to 28.9.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=8cm]{DemBoxplot.png}
+    \caption{Box plots of the DEM Results of the Reduce Overlap}
+    \label{fig:BoxPlot_unscaled}
+\end{figure}
+
+Figure \ref{fig:DemPlot_scaled} contains the same visualization of DEM plots, only for all the DEM's the data has been scaled.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=8cm]{DemPlots_scaled.png}
+    \caption{Scaled DEM Results of the Reduce Overlap}
+    \label{fig:DemPlot_scaled}
+\end{figure}
+
+The same applies for figure \ref{fig:BoxPlot_unscaled}, only now the boxplot contain the scaled data values.
+
+\begin{figure}[htp]
+    \centering
+    \includegraphics[width=8cm]{DemBoxPlot_Scaled.png}
+    \caption{Scaled DEM Results of the Reduce Overlap}
+    \label{fig:BoxPlot_scaled}
+\end{figure}
+
 \section{Discussion}
+The goal of this research was to assess the difference between DEM's of the same area with different image overlap. 
+The image reduction in the paper was calculated in Agisoft Metashape with the Reduce Overlap function.
 The amount of images used in the processing does not seem to influence the density of the dense cloud, which was also concluded by \citet{EffectofUABimgcamover}.
+In this research the point confidence was not measured, the dense cloud were directly used to construct a DEM.
+
 The input mesh for the Reduce Overlap was a 2.5D height field. 
 With more complex objects that need to processed as a real 3D object the amount of dense cloud may decrease if the amount of images is reduces significantly.
+Because the mesh was structured as a 2.5D surface, difficult points were removed from the model, e.g. in this case the tree structures were lost in the process.
 An other option is that the Reduce Overlap function will not have much influence on the image count.
+
+There is a large different between the absolute values between the different DEM's, this can be seen visually in figure \ref{fig:DemPlot_unscaled} and also when comparing the boxplot values in figure \ref{fig:BoxPlot_unscaled}.
+With the use of at least three ground control points the error in the absolute values of the can be prevented \citep{AssessingUAVGCPS}.
+By using GCP's
 

### 2021-04-21 Paper.tex
finalbackup2104

@@
 
-\textbf{Camera Location.}
+\textbf{Camera Locations.}
 In figure \ref{fig:cameralocation} the estimated camera locations can be found.
 The camera selection is done by the Reduce Overlap algorithm from Agisoft Metashape.
-The estimated camera location is done in the image processing.
+The estimated camera location is done in the image processing alogrithm of Metashape.
 The images are matched based on an adapted version of the SIFT algorithm \citep{lowe1999object, AgisoftMetashape}.
@@
     White: used in the image processing, red: disabled in the image processing.\\
-    Clockwise: low, medium, high and full settings}
+    Clockwise (starting left top): low, medium, high and full settings}
     \label{fig:cameralocation}
@@
 There is a large different between the absolute values between the different DEM's, this can be seen visually in figure \ref{fig:DemPlot_unscaled} and also when comparing the boxplot values in figure \ref{fig:BoxPlot_unscaled}.
-With the use of at least three ground control points the error in the absolute values of the can be prevented \citep{AssessingUAVGCPS}.
-By using GCP's
+With the use of at least three ground control points the error in the absolute values of the can be reduced \citep{AssessingUAVGCPS, GCPbetterAccuracy}.
 
 \section{Conclusion}
+Using different image overlap in the same area results in DEM's with different absolute values.
+The two image dataset with the least images show the largest difference in absolute value range compared to the original dataset with all images. 
+The image dataset with the highest image count, has a DEM that is most similar compared to the original dataset.
+When the scaled values are compared there seems to be a minimal difference between the DEM's
 

### 2021-04-23 Paper.tex
20200423 backup

@@
 There are a few trees present.
-\begin{figure}[htp]
+\begin{figure}[h]
     \centering
@@
 For image processing and DEM generation Agisoft Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used \citep{AgisoftMetashape}.
+All data have been processed on the cloud service provided by Agisoft (\url{https://cloud.agisoft.com}).
+The cloud processing is done on a vCPU (Intel Xeon E5 2686 v4) with two NVIDIA Tesla M60 GPU's and 240 GB of RAM.
+
 First, the complete data set has been aligned on medium quality.
@@
 
-\begin{figure}[htp]
+\begin{figure}[h]
     \centering
@@
 
-\begin{table}[htb]
+\begin{table}[h]
     \centering
@@
     High   & 75  & 49,692 & 3,276,832 \\ \bottomrule
+    % Add processing time!
     \label{tab:ImageProcessing}
+\end{tabular}
+\end{table}
+
+For all the different settings the processing time can be found in table \ref{tab:processingTime}
+
+\begin{table}[h]
+    \centering
+    \caption{Processing time in seconds for the difference steps in the process.}
+    \label{tab:processingTime}
+    \begin{tabular}{@{}cccc@{}}
+    \toprule
+    \textbf{Setting} & \textbf{Sparse Cloud} & \multicolumn{1}{l}{\textbf{Dense Cloud}} & \multicolumn{1}{l}{\textbf{DEM}} \\ 
+    \midrule
+    -      & 150 & 292 & 17 \\
+    Low    & 59  & 443 & 16 \\
+    Medium & 83  & 147 & 17 \\
+    High   & 129 & 159 & 17 \\ \bottomrule
 \end{tabular}
@@
 Because of this the largest common extent of the DEM's will be used to crop the DEM's resulting in four DEM's with an equal extent.
+The DEM's will be exported from Agisoft Metashape with the same pixel resolution of 17.5 cm per pixel.
 The DEM's will also be scaled to check the differences between the DEM's without looking at the absolute values.
 The scaling will be done by subtracting the mean and dividing by the standard deviation.
+For further comparison all of the DEM's will be subtracted from the full model DEM.
+This will result in three new DEM's that contain differences instead of height values.
 
@@
 \end{figure}
+
+In figure \ref{fig:ViolinPlot} a violin plot containing the difference of the DEM between the different Reduce Overlap settings can be found.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=8cm]{ViolinPlot2.png}
+    \caption{Violin plot of the difference between the full DEM and the reduced DEM's}
+    \label{fig:ViolinPlot}
+\end{figure}
+
+% Substract the DEM from each other
 

### 2021-04-24 Paper.tex
20200424 backup

@@
 The digital elevation models are compared to see how reducing the image overlap influences the result. 
+A boxplot has been made to compare to the absolute values of the DEM's.
+Large difference are visible, however when the scaled DEM's are plotted in a boxplot the difference appear to be minimal.
+Finally a violin plot has been made of the complete image set DEM minus the reduces image set DEM's.
+The more images are used, the more the difference of the DEM's is centered around 0.
 }
@@
 The area of interest is about 25000 m\textsuperscript{2}. 
-The area consists mostly of sanvannah.
-There are a few trees present.
+The area consists mostly of savanna area.
+There are a few trees present on the observed location.
 \begin{figure}[h]
@@
 All data have been processed on the cloud service provided by Agisoft (\url{https://cloud.agisoft.com}).
-The cloud processing is done on a vCPU (Intel Xeon E5 2686 v4) with two NVIDIA Tesla M60 GPU's and 240 GB of RAM.
+The cloud processing is done on 32 vCPU's (Intel Xeon E5 2686 v4) with two NVIDIA Tesla M60 GPU's and 240 GB of RAM.
 
@@
 A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
-After the mesh the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
+finally after the mesh the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
 The mesh was set to create a 2.5D height field.
@@
 In Agisoft Metashape the 'Reduce Overlap' had three different settings, low, medium and high. 
-All of the settings are used to compute the images for further processing.
+All of the settings are used and the remaining images are used for further processing.
+In \ref{tab:ImageProcessing} the amount of images for each Reduce Overlap setting can be found.
 
 \textbf{Camera Locations.}
-In figure \ref{fig:cameralocation} the estimated camera locations can be found.
-The camera selection is done by the Reduce Overlap algorithm from Agisoft Metashape.
-The estimated camera location is done in the image processing alogrithm of Metashape.
+In figure \ref{fig:cameralocation} the estimated camera locations can be found. The estimated camera location is estimated by the image processing alogrithm of Metashape.
 The images are matched based on an adapted version of the SIFT algorithm \citep{lowe1999object, AgisoftMetashape}.
@@
     \centering
-    \includegraphics[width=4cm]{loc_low.png}
-    \includegraphics[width=4cm]{loc_med.png}
-    \includegraphics[width=4cm]{loc_full.png}
-    \includegraphics[width=4cm]{loc_high.png}
+    \includegraphics[width=1.9cm]{loc_low.png}
+    \includegraphics[width=1.9cm]{loc_med.png}
+    \includegraphics[width=1.9cm]{loc_high.png}
+    \includegraphics[width=1.9cm]{loc_full.png}
     \caption{Estimated camera location. 
@@
 
-\subsection{DEM}
+\textbf{DEM.}
 The source data for the DEM's are the dense cloud results. 
@@
 In figure \ref{fig:ViolinPlot} a violin plot containing the difference of the DEM between the different Reduce Overlap settings can be found. 
+It is visible that the overall error of the scaled DEM's varies from around -5.0 to 5.0.
+For the high settings, the differences are more centered around zero, while this is not the case for low and medium settings.
+For medium setting the difference is slightly more centered around 0.0 than low settings.
 
@@
     \centering
-    \includegraphics[width=8cm]{ViolinPlot2.png}
+    \includegraphics[width=8cm]{ViolinPlotOrdered.png}
     \caption{Violin plot of the difference between the full DEM and the reduced DEM's}
@@
 With the use of at least three ground control points the error in the absolute values of the can be reduced \citep{AssessingUAVGCPS, GCPbetterAccuracy}.
+Using GCP's in the different image dataset will reduce the absolute error, further research is needed how much is influence the relative error of the different DEM's
 
@@
 The image dataset with the highest image count, has a DEM that is most similar compared to the original dataset.
-When the scaled values are compared there seems to be a minimal difference between the DEM's
+When the scaled values are compared there seems to be a minimal difference between the DEM's.
+If more images are used in the dataset, the difference between the DEM's compared to the full images set becomes smaller; the DEM differences are more centered around 0.
 

### 2021-04-26 Paper.tex
20200426 backup

@@
 \abstract{
-Photogrammetry is easy to use these days and can be used to create a digital elevation model of an area. 
+Photogrammetry is easy to use these days and can be used to create a digital elevation models (DEM) of an area. 
 Image overlap plays an important role in the process of photogrammetry.
@@
 The digital elevation models are compared to see how reducing the image overlap influences the result. 
-A boxplot has been made to compare to the absolute values of the DEM's.
-Large difference are visible, however when the scaled DEM's are plotted in a boxplot the difference appear to be minimal.
+When the absolute values of the DEM in compared large differences are visible.
+However, when the scaled DEM's are compared in a boxplot the differences appear to be minimal.
 Finally a violin plot has been made of the complete image set DEM minus the reduces image set DEM's.
 The more images are used, the more the difference of the DEM's is centered around 0.
+The DEM of the dataset with the highest images count seems to be the most similar to the DEM of the full dataset.
 }
@@
 Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
-The process uses similar points visible on multiple images to determine the points in space.
+These days most photogrammetry data is acquired with unmanned aerial vehicles (UAV) \citet{UAVAreMoreUsed}. 
+UAV's come with GNSS and provide high resolution images needed for photogrammetry.
+The process uses similar points visible on multiple images to determine the points in 3D space.
 The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
-When a point is visible on more images, the reconstruction certainty will be higher.
-This is especially the case with the reconstruction of irregular formed object like vegetation \citep{AccessingImageOverlap}.
-With irregular objects, a higher overlap is preferred to capture each side of the object.
-If parts of the object are not visible on the image, they will not be reconstructed in the point cloud.
-So the overlap strongly influences the point cloud density in the dense cloud \citep{OptimalAltOverWeath}.
+Because most programs handle 2D data better than 3D data, the point cloud is usually used to build a digital elevation model (DEM) \citet{DemIncrease1}.
+
+A higher image overlap results in more similar image points which will increase the reconstruction certainty of the points \citep{MoreOverMoreAcc}.
+A higher image overlap, does not automatically results in a denser point cloud. \citep{EffectofUABimgcamover}. 
+A high overlap is needed in complex structures like vegatetion; if parts of the object are not visible on the image, they will not be reconstructed in the point cloud \citep{AccessingImageOverlap}.
+However, an image dataset with a high overlap takes longer to gather, and may results in multiple drone flights for a single dataset \citep{UAVpopularity}.
 In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
-However, a higher image overlap, does not automatically results in a higher point accuracy (x,y,z) \citep{EffectofUABimgcamover}. 
-With the development of cheap Unmanned Aerial Vehicles (UAV) photogrammetry has become more and more popular \citet{UAVAreMoreUsed}. 
-UAV's come with high resolution cameras, GNSS and are available almost anywhere these days.
-While UAV's do come with high resolution sensors and relatively cheap, small, high capacity batteries are not available \citep{UAVpopularity}.
-A high image overlap takes longer to gather than a low image overlap. 
-A drone can use a higher altitude so the sensor captures a larger area.
-however, with a higher flight altitude the detail of the image will be less than that of a drone with a lower flight altitude.
-This way the gathering process takes longer, and the UAV might even need to switch batteries instead of taking the images in a single flight.
 By reducing the image overlap, time and computing power may be saved without loosing too much spatial information.
@@
 Because of this the largest common extent of the DEM's will be used to crop the DEM's resulting in four DEM's with an equal extent.
-The DEM's will be exported from Agisoft Metashape with the same pixel resolution of 17.5 cm per pixel.
+The DEM's will be exported from Agisoft Metashape with the same pixel resolution of 17.5 cm per pixel (1670 x 1290 pixels). 
 The DEM's will also be scaled to check the differences between the DEM's without looking at the absolute values.
@@
 The outliers in the boxplot figure are probably the vegetation that is present in the area.
-For the low setting the DEM values range from -19.4 to 19.0, for the medium setting the values range from -22.7 to 16.2, for the high setting the values range from 13.1 to 20.0 and for the full model from -4.8 to 28.9.
+%For the low setting the DEM values range from -19.4 to 19.0, for the medium setting the values range from -22.7 to 16.2, for the high setting the values range from 13.1 to 20.0 and for the full model from -4.8 to 28.9.
 
@@
     \includegraphics[width=8cm]{ViolinPlotOrdered.png}
-    \caption{Violin plot of the difference between the full DEM and the reduced DEM's}
+    \caption{Violin plot of the difference between the full DEM and the reduced DEM's. All violin plots contain 2.154.300 measurements (DEM rows x DEM columns}
     \label{fig:ViolinPlot}
@@
 There is a large different between the absolute values between the different DEM's, this can be seen visually in figure \ref{fig:DemPlot_unscaled} and also when comparing the boxplot values in figure \ref{fig:BoxPlot_unscaled}.
-With the use of at least three ground control points the error in the absolute values of the can be reduced \citep{AssessingUAVGCPS, GCPbetterAccuracy}.
-Using GCP's in the different image dataset will reduce the absolute error, further research is needed how much is influence the relative error of the different DEM's
+With the use of at least three ground control points the error in the absolute values of the can be reduced \citep{AssessingUAVGCPS, GCPbetterAccuracy, GeoreferencedPointClouds}.
+Using GCP's in the different image dataset will reduce the absolute error.
+
+The violin plots indicate that the dataset with the highest image count is most similar to the full dataset; the difference of is more centered around zero, while the two lower image count datasets are more widespread (higher SD).
+The largest errors difference (around -5/5) between the scaled DEM seem to be the same for all the image datasets.
+The modelling software probably has difficulties in modelling the complex structures of the vegetation, resulting in a larger difference when the image count is lower.
+This could result in more error around vegetation canopies where the algorithm has difficulties in accurately measuring the height.
+An other option may changing the filtering setting provided by the Metashape dense cloud generation.
+In this research no depth filtering was used, by applying a more aggressive filtering technique the complex structures of the vegetation will be lost in the DEM generation \citep{AgisoftMetashape}.
+Further research is needed to see where this differences exactly occur and if a different depth filtering may result in different results.
 
@@
 When the scaled values are compared there seems to be a minimal difference between the DEM's.
-If more images are used in the dataset, the difference between the DEM's compared to the full images set becomes smaller; the DEM differences are more centered around 0.
+If more images are used in the dataset, the difference between the scaled DEM's compared to the full images set becomes smaller; the DEM differences are more centered around 0.
 
@@
 \end{document}
+
+Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
+The process uses similar points visible on multiple images to determine the points in 3D space.
+The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
+When a point is visible on more images, the reconstruction certainty will be higher \citep{MoreOverMoreAcc}.
+This is especially the case with the reconstruction of irregular formed object like vegetation \citep{AccessingImageOverlap}.
+With irregular objects, a higher overlap is preferred to capture each side of the object.
+If parts of the object are not visible on the image, they will not be reconstructed in the point cloud.
+In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
+However, a higher image overlap, does not automatically results in a denser point cloud. \citep{EffectofUABimgcamover}. 
+These days most photogrammetry data is acquired with Unmanned Aerial Vehicles (UAV) \citet{UAVAreMoreUsed}. 
+UAV's come with high resolution cameras, GNSS and are available almost anywhere these days.
+While UAV's do come with high resolution sensors and are relatively cheap, small, high capacity batteries are not available \citep{UAVpopularity}.
+A high image overlap takes longer to gather than a low image overlap. 
+A drone can use a higher altitude so the sensor captures a larger area.
+however, with a higher flight altitude the detail of the image will be less than that of a drone with a lower flight altitude.
+This way the gathering process takes longer, and the UAV might even need to switch batteries instead of taking the images in a single flight.
+By reducing the image overlap, time and computing power may be saved without loosing too much spatial information.
+This main goal of this study is to investigate how different image overlap influence the DEM result that is created with photogrammetry.

### 2021-04-27 Paper.tex
20210427 backup (draft)

@@
 \usepackage{fancyref}
+\pagestyle{plain}
 
@@
 In this paper the overlap of an area is artificially reduced and digital elevation models have been created with different image overlaps.
-The digital elevation models are compared to see how reducing the image overlap influences the result. 
+The digital elevation models (DEM) are compared to see how reducing the image overlap influences the result. 
 When the absolute values of the DEM in compared large differences are visible.
 However, when the scaled DEM's are compared in a boxplot the differences appear to be minimal.
-Finally a violin plot has been made of the complete image set DEM minus the reduces image set DEM's.
+Finally, violin plots have been made of the complete image set DEM minus the reduces image set DEM's.
 The more images are used, the more the difference of the DEM's is centered around 0.
@@
 The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
-Because most programs handle 2D data better than 3D data, the point cloud is usually used to build a digital elevation model (DEM) \citet{DemIncrease1}.
+A digital elevation model (DEM) is a popular product from photogrammetry \citet{DemIncrease1}.
+A DEM is a 2D grid containing height values and is frequently used in geoinformation applications.
+It is therefore important to create high quality DEM's.
 
-A higher image overlap results in more similar image points which will increase the reconstruction certainty of the points \citep{MoreOverMoreAcc}.
+A higher image overlap results in more similar image points, which will increase the reconstruction certainty of the points \citep{MoreOverMoreAcc}.
 A higher image overlap, does not automatically results in a denser point cloud. \citep{EffectofUABimgcamover}. 
-A high overlap is needed in complex structures like vegatetion; if parts of the object are not visible on the image, they will not be reconstructed in the point cloud \citep{AccessingImageOverlap}.
+A high overlap is needed in complex structures like vegetation; if parts of the object are not visible on the image, they will not be reconstructed in the point cloud \citep{AccessingImageOverlap}.
 However, an image dataset with a high overlap takes longer to gather, and may results in multiple drone flights for a single dataset \citep{UAVpopularity}.
@@
 The data covers an area in Ghana, about 20km south east of Ejura (lat. 7.3064212, lon. -1.164493). 
-The area of interest is about 25000 m\textsuperscript{2}. 
-The area consists mostly of savanna area.
+The area of interest is about 25000 m\textsuperscript{2} and consists mostly of savanna area.
 There are a few trees present on the observed location.
+Each image has a resolution of 4000 times 3000 and was taken by a DJI Phantom 3.
+The images all contain a GNNS location (WGS84). 
+The complete data set consists of 111 images.
+Their exact location can be found in figure \ref{fig:areaofinterest}.
 \begin{figure}[h]
@@
 \end{figure}
-Each image has a resolution of 4000 times 3000 and was taken by a DJI Phantom 3.
-The images all contain GNNS location (WGS84). 
-The complete data set consists of 111 images.
-Their exact location can be found in figure \ref{fig:areaofinterest}.
 
 \subsection{Image Processing}
-For image processing and DEM generation Agisoft Professional edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used \citep{AgisoftMetashape}.
+For image processing and DEM generation Agisoft Professional Edition 1.6.5 (Agisoft LLC., St. Peterburg, Russia) was used \citep{AgisoftMetashape}.
 All data have been processed on the cloud service provided by Agisoft (\url{https://cloud.agisoft.com}).
@@
 First, the complete data set has been aligned on medium quality.
+On medium alignment quality the original images are scaled to have 1/2 of the original size.
 Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.
+With medium settings the original photo is scaled to 1/4 before used in the dense cloud generation process.
 A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
-finally after the mesh the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
-The mesh was set to create a 2.5D height field.
+finally after the mesh, the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
+Because the final product of the photogrammetry process in this paper is a DEM a 2.5D height field was used when the mesh was generated
+The 2.5D height field mesh contains only one Z value for any X, Y coordinate combination, this is also the case in the final DEM.
 
@@
 If a point is observed multiple times from the same location/angle, than this still counts as one. 
-The exact algorithm and parameters behind the Agisoft Reduce Overlap function are unknown.
-The input dataset was a 2.D height field mesh. 
-Because in this paper the comparison will be made with a DEM, a height field was computed.
-In Agisoft Metashape the 'Reduce Overlap' had three different settings, low, medium and high. 
+As in this research a height field was used, the algorithm will probably take the vegetation canopy into account in the reconstruction, but lower branches may be lost in the process.
+This will has some influence on the Reduce Overlap setting; it becomes more flexible because single height values are for each X, Y coordinate combination is used.
+The algorithm and parameters behind the Agisoft Reduce Overlap function are proprietary software and therefore unfortunately unknown.
+In Agisoft Metashape the Reduce Overlap had three different settings, low, medium and high. 
 All of the settings are used and the remaining images are used for further processing.
-In \ref{tab:ImageProcessing} the amount of images for each Reduce Overlap setting can be found.
+In table \ref{tab:ImageProcessing} the result of each Reduce Overlap settings can be found.
+The images available in table \ref{tab:ImageProcessing} will be treated as a unique dataset and will be used in the image processing pipeline from Agisoft.
 
 \textbf{Camera Locations.}
-In figure \ref{fig:cameralocation} the estimated camera locations can be found. The estimated camera location is estimated by the image processing alogrithm of Metashape.
+After all the new datasets with the images have been aligned the camera locations are estimated, in figure \ref{fig:cameralocation} camera locations can be found. 
 The images are matched based on an adapted version of the SIFT algorithm \citep{lowe1999object, AgisoftMetashape}.
+All the datasets are processed on medium settings for the image alignment.
+None of the images used in the alignment process failed to align.
 
@@
     \caption{Estimated camera location. 
-    White: used in the image processing, red: disabled in the image processing.\\
-    Clockwise (starting left top): low, medium, high and full settings}
+    White: used in the image processing, red: disabled in the image processing.
+    Starting left: low, medium, high and full settings}
     \label{fig:cameralocation}
@@
 
-After the amount of images have been reduced, the data have been processed on medium for the image alignment and on medium without depth filtering for the dense cloud creation.
+\textbf{Dense Cloud.}
+The result of the alignment of the images is used as input for the dense cloud generation.
+The data has been processing on medium  settings without any depth filtering for the generation of the dense cloud.
+
 In table \ref{tab:ImageProcessing} an overview of the image processing results can be found.
@@
 
-For all the different settings the processing time can be found in table \ref{tab:processingTime}
+For all the different datasets the processing time can be found in table \ref{tab:processingTime}.
 
@@
 The source data for the DEM's are the dense cloud results. 
-The Dense Cloud contains about the same amount of points with the exception for the lowest Reduce Overlap setting.
-This setting has resulted in the dense cloud with the most points.
+The dense clouds contain about the same amount of points with the exception for the lowest Reduce Overlap setting, This setting has resulted in the dense cloud with the most points.
 The TIN algorithm is used to built the DEM's \citep{axelsson1999processing}.
-The image overlap is now changed, therefore the DEM's have a slightly different extent.
-Because of this the largest common extent of the DEM's will be used to crop the DEM's resulting in four DEM's with an equal extent.
-The DEM's will be exported from Agisoft Metashape with the same pixel resolution of 17.5 cm per pixel (1670 x 1290 pixels). 
+Because the dense clouds are unique the TIN algorithm also results in four unique DEM's.
+These DEM's all have a slightly different extent and resolution.
+For further comparison the DEM's have all been cropped on the largest common extent and the pixel resolution was set to 17.5 cm per pixel (1670 x 1290 pixels).
 The DEM's will also be scaled to check the differences between the DEM's without looking at the absolute values.
@@
 This will result in three new DEM's that contain differences instead of height values.
+These data will be used to inspect the differences between the scaled DEM of the full image dataset and the scaled DEM's of the other datasets.
 
 \section{Results}
-In figure \ref{fig:DemPlot_unscaled} are visualized using the same color range. 
+In figure \ref{fig:DemPlot_unscaled} the DEM's are visualized using the same color range. 
 In this figure the DEM's do no look similar at all.
@@
 As can be seen from figure \ref{fig:BoxPlot_unscaled} the DEM's are indeed different from each other. 
-The outliers in the boxplot figure are probably the vegetation that is present in the area.
-%For the low setting the DEM values range from -19.4 to 19.0, for the medium setting the values range from -22.7 to 16.2, for the high setting the values range from 13.1 to 20.0 and for the full model from -4.8 to 28.9.
+For the low setting the DEM values range from -19.4 to 19.0, for the medium setting the values range from -22.7 to 16.2, for the high setting the values range from 13.1 to 20.0 and for the full model from -4.8 to 28.9.
 
@@
 Figure \ref{fig:DemPlot_scaled} contains the same visualization of DEM plots, only for all the DEM's the data has been scaled.
+There is almost no visual difference visible in the figure, the DEM's look quite similar.
 
@@
 
-The same applies for figure \ref{fig:BoxPlot_unscaled}, only now the boxplot contain the scaled data values.
+The same applies for figure \ref{fig:BoxPlot_scaled}, only now the boxplot contain the scaled data values.
+There difference seem to be minimal in the scaled boxplots.
 
@@
 
-In figure \ref{fig:ViolinPlot} a violin plot containing the difference of the DEM between the different Reduce Overlap settings can be found. 
+Figure \ref{fig:ViolinPlot} contains three violin plots. For each of the plots the scaled DEM's from the reduces image datasets has been subtracted from the scaled full dataset DEM.
 It is visible that the overall error of the scaled DEM's varies from around -5.0 to 5.0.
@@
     \includegraphics[width=8cm]{ViolinPlotOrdered.png}
-    \caption{Violin plot of the difference between the full DEM and the reduced DEM's. All violin plots contain 2.154.300 measurements (DEM rows x DEM columns}
+    \caption{Violin plot of the difference between the full DEM and the reduced DEM's. All violin plots contain 2.154.300 measurements (1.670 rows x 1.290 columns)}
     \label{fig:ViolinPlot}
 \end{figure}
-
-% Substract the DEM from each other
 
@@
 
-The input mesh for the Reduce Overlap was a 2.5D height field. 
-With more complex objects that need to processed as a real 3D object the amount of dense cloud may decrease if the amount of images is reduces significantly.
-Because the mesh was structured as a 2.5D surface, difficult points were removed from the model, e.g. in this case the tree structures were lost in the process.
-An other option is that the Reduce Overlap function will not have much influence on the image count.
+%The input mesh for the Reduce Overlap was a 2.5D height field. 
+%This could be of influence, because the 2.5D mesh only takes one single height value into account for each %X, Y combination.
+
+%With more complex objects that need to processed as a real 3D object the quality of dense cloud may decrease if the amount of images is reduces significantly.
+%Because the mesh was structured as a 2.5D surface, difficult points were removed from the model, e.g.
+in this case the tree canopies were constructed, but e.g.
+lower branches were lost in the construction process.
+%An other option is that the Reduce Overlap function will not have much influence on the image count.
 
 There is a large different between the absolute values between the different DEM's, this can be seen visually in figure \ref{fig:DemPlot_unscaled} and also when comparing the boxplot values in figure \ref{fig:BoxPlot_unscaled}.
+The outliers in both boxplot figures are probably the vegetation that is present in the area as the boxplots only contain high outliers.
 With the use of at least three ground control points the error in the absolute values of the can be reduced \citep{AssessingUAVGCPS, GCPbetterAccuracy, GeoreferencedPointClouds}.
@@
 
-The violin plots indicate that the dataset with the highest image count is most similar to the full dataset; the difference of is more centered around zero, while the two lower image count datasets are more widespread (higher SD).
-The largest errors difference (around -5/5) between the scaled DEM seem to be the same for all the image datasets.
+The violin plots indicate that the dataset with the highest image count is most similar to the full dataset; the difference of is more centered around zero, while the two lower image count datasets are more widespread.
+The largest errors differences (around -5/5) between the scaled DEM seem to be the same for all the image datasets.
 The modelling software probably has difficulties in modelling the complex structures of the vegetation, resulting in a larger difference when the image count is lower.
 This could result in more error around vegetation canopies where the algorithm has difficulties in accurately measuring the height. 
+\citet{AccessingImageOverlap} also concluded that for complex structures a higher image overlap provides better results.
 An other option may changing the filtering setting provided by the Metashape dense cloud generation.

### 2021-04-29 Draft.tex
Backup 20210429

--- 2021-04-27 Paper.tex
@@
 % KAO: Remove extra spacing
-\author{Robert van de Vlasakker}
+\author{Robert van de Vlasakker\textsuperscript{a}}
 
 % KAO: Remove extra newline
-\address{} % Not needed
+\address{
+    \textsuperscript{a}
+    Wageningen University \& Research} % Not needed
 
@@
 In this paper the overlap of an area is artificially reduced and digital elevation models have been created with different image overlaps.
-The digital elevation models (DEM) are compared to see how reducing the image overlap influences the result. 
-When the absolute values of the DEM in compared large differences are visible.
+The DEM's are compared to see how reducing the image overlap influences the result. 
+When the absolute values of the DEM are compared large differences are visible.
 However, when the scaled DEM's are compared in a boxplot the differences appear to be minimal.
@@
 Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
-These days most photogrammetry data is acquired with unmanned aerial vehicles (UAV) \citet{UAVAreMoreUsed}. 
+These days most photogrammetry data is acquired with unmanned aerial vehicles (UAV) \citep{UAVAreMoreUsed}. 
 UAV's come with GNSS and provide high resolution images needed for photogrammetry.
@@
 The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
-A digital elevation model (DEM) is a popular product from photogrammetry \citet{DemIncrease1}.
+A digital elevation model (DEM) is a popular product from photogrammetry \citep{DemIncrease1}.
 A DEM is a 2D grid containing height values and is frequently used in geoinformation applications.
@@
 A high overlap is needed in complex structures like vegetation; if parts of the object are not visible on the image, they will not be reconstructed in the point cloud \citep{AccessingImageOverlap}.
-However, an image dataset with a high overlap takes longer to gather, and may results in multiple drone flights for a single dataset \citep{UAVpopularity}.
+However, an image dataset with a high overlap takes longer to gather, and may require multiple drone flights for a single dataset \citep{uavpop}.
 In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
 By reducing the image overlap, time and computing power may be saved without loosing too much spatial information.
-This main goal of this study is to investigate how different image overlap influence the DEM result that is created with photogrammetry.
+%The goal of this study is to investigate the results on the image processing results of using reduced image sets of the same area. 
+This main goal of this study is to investigate how different image overlap influences the DEM result that is created with photogrammetry.
+It will be investigated how the different image overlap influence the intermediate photogrammetry results and processing time.
 

### 2021-04-29 Paper.tex
Updates from Overleaf

@@
 \usepackage[hang]{footmisc}
+%\setlength{\tabcolsep}{2pt}
 \def\footnotemargin{1em} % added 08-01-2020 Dennis Wittich
@@
 On medium alignment quality the original images are scaled to have 1/2 of the original size.
+%ADD MANUAL
 Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.
 With medium settings the original photo is scaled to 1/4 before used in the dense cloud generation process.
+%ADD MANUAL
 A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
@@
 As in this research a height field was used, the algorithm will probably take the vegetation canopy into account in the reconstruction, but lower branches may be lost in the process.
-This will has some influence on the Reduce Overlap setting; it becomes more flexible because single height values are for each X, Y coordinate combination is used.
+This will have some influence on the Reduce Overlap setting; it becomes more flexible because single height values are used for each X, Y coordinate combination.
 The algorithm and parameters behind the Agisoft Reduce Overlap function are proprietary software and therefore unfortunately unknown.
@@
 All of the settings are used and the remaining images are used for further processing.
-In table \ref{tab:ImageProcessing} the result of each Reduce Overlap settings can be found.
-The images available in table \ref{tab:ImageProcessing} will be treated as a unique dataset and will be used in the image processing pipeline from Agisoft.
-
-\textbf{Camera Locations.}
-After all the new datasets with the images have been aligned the camera locations are estimated, in figure \ref{fig:cameralocation} camera locations can be found. 
 The images are matched based on an adapted version of the SIFT algorithm \citep{lowe1999object, AgisoftMetashape}.
 All the datasets are processed on medium settings for the image alignment.
-None of the images used in the alignment process failed to align.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=1.9cm]{loc_low.png}
-    \includegraphics[width=1.9cm]{loc_med.png}
-    \includegraphics[width=1.9cm]{loc_high.png}
-    \includegraphics[width=1.9cm]{loc_full.png}
-    \caption{Estimated camera location. 
-    White: used in the image processing, red: disabled in the image processing.
-    Starting left: low, medium, high and full settings}
-    \label{fig:cameralocation}
-\end{figure}
 
@@
 
-In table \ref{tab:ImageProcessing} an overview of the image processing results can be found.
+\textbf{DEM.}
+The source data for the DEM's are the dense cloud results. 
+The TIN algorithm is used to built the DEM's \citep{axelsson1999processing}.
+Because the dense clouds are unique the TIN algorithm also results in four unique DEM's.
+These DEM's all have a slightly different extent and resolution.
+For further comparison the DEM's have all been cropped on the largest common extent and the pixel resolution was set to 17.5 cm per pixel (1670 x 1290 pixels).
+The DEM's were also be scaled to check the differences between the DEM's without looking at the absolute values.
+The scaling was be done by subtracting the mean and dividing by the standard deviation.
+For further comparison all of the DEM's were be subtracted from the full model DEM.
+%%% CHECK THIS
+These data will be used to inspect the differences between the scaled DEM of the full image dataset compared to the other DEM's.
+
+\section{Results}
+In table \ref{tab:ImageProcessing} the result of image processing for each Reduce Overlap settings can be found. 
+The dense clouds contain about the same amount of points with the exception for the lowest Reduce Overlap setting, This setting has resulted in the dense cloud with the most points.
 
@@
     \toprule
-    \textbf{Setting} & \textbf{Images} & \multicolumn{1}{l}{\textbf{Sparse Cloud}} & \multicolumn{1}{l}{\textbf{Dense Cloud}} \\ \midrule
+    \textbf{\begin{tabular}[c]{@{}c@{}}Reduce Overlap \\ Setting\end{tabular}} &
+    \textbf{\begin{tabular}[c]{@{}c@{}}Image\\ Count\end{tabular}} &
+    \textbf{Sparse  Cloud} &
+    \textbf{Dense Cloud} \\ \midrule
     -      & 111 & 80,901 & 3,269,264 \\
@@
     \toprule
-    \textbf{Setting} & \textbf{Sparse Cloud} & \multicolumn{1}{l}{\textbf{Dense Cloud}} & \multicolumn{1}{l}{\textbf{DEM}} \\ 
-    \midrule
-    -      & 150 & 292 & 17 \\
-    Low    & 59  & 443 & 16 \\
-    Medium & 83  & 147 & 17 \\
-    High   & 129 & 159 & 17 \\ \bottomrule
+    \textbf{Image Count} & \textbf{Sparse  Cloud} & \textbf{Dense Cloud} & \textbf{Dem} \\ \midrule
+    111                  & 150                    & 292                  & 17           \\
+    44                   & 59                     & 443                  & 16           \\
+    70                   & 83                     & 147                  & 17           \\
+    75                   & 129                    & 159                  & 17           \\ \bottomrule
     \end{tabular}
@@
 
-\textbf{DEM.}
-The source data for the DEM's are the dense cloud results. 
-The dense clouds contain about the same amount of points with the exception for the lowest Reduce Overlap setting, This setting has resulted in the dense cloud with the most points.
-The TIN algorithm is used to built the DEM's \citep{axelsson1999processing}.
-Because the dense clouds are unique the TIN algorithm also results in four unique DEM's.
-These DEM's all have a slightly different extent and resolution.
-For further comparison the DEM's have all been cropped on the largest common extent and the pixel resolution was set to 17.5 cm per pixel (1670 x 1290 pixels).
-The DEM's will also be scaled to check the differences between the DEM's without looking at the absolute values.
-The scaling will be done by subtracting the mean and dividing by the standard deviation.
-For further comparison all of the DEM's will be subtracted from the full model DEM.
-This will result in three new DEM's that contain differences instead of height values.
-These data will be used to inspect the differences between the scaled DEM of the full image dataset and the scaled DEM's of the other datasets.
+After all the new datasets with the images have been aligned the camera locations are estimated, in figure \ref{fig:cameralocation} camera locations can be found. 
+None of the images used in the alignment process failed to align.
 
-\section{Results}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.9cm]{loc_low.png}
+    \includegraphics[width=1.9cm]{loc_med.png}
+    \includegraphics[width=1.9cm]{loc_high.png}
+    \includegraphics[width=1.9cm]{loc_full.png}
+    \caption{Estimated camera location. 
+    White: used in the image processing, red: disabled in the image processing.
+    Starting left: low, medium, high and full settings}
+    \label{fig:cameralocation}
+\end{figure}
+
 In figure \ref{fig:DemPlot_unscaled} the DEM's are visualized using the same color range. 
@@
     \centering
-    \includegraphics[width=8cm]{DemPlots.png}
+    \includegraphics[width=8.5cm]{DemPlots.png}
     \caption{DEM Results of the Reduce Overlap}
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
     \centering
@@
 There is almost no visual difference visible in the figure, the DEM's look quite similar.
+This is confirmed in figure \ref{fig:BoxPlot_scaled}, only now the boxplot contain the scaled data values.
+These difference seem to be minimal in the scaled boxplots.
 
@@
 
-The same applies for figure \ref{fig:BoxPlot_scaled}, only now the boxplot contain the scaled data values.
-There difference seem to be minimal in the scaled boxplots.
-
 \begin{figure}[h]
@@
 
-Figure \ref{fig:ViolinPlot} contains three violin plots. For each of the plots the scaled DEM's from the reduces image datasets has been subtracted from the scaled full dataset DEM.
-It is visible that the overall error of the scaled DEM's varies from around -5.0 to 5.0.
+Figure \ref{fig:ViolinPlot} contains three violin plots. For each of the plots the scaled DEM's from the reduced image datasets has been subtracted from the scaled full dataset DEM.
+It is visible that the overall scaled error difference of the scaled DEM's varies from around -5.0 to 5.0.
 For the high settings, the differences are more centered around zero, while this is not the case for low and medium settings.

### 2021-05-01 Paper.tex
20210501 backup

@@
 Less overlap usually results in a less accurate calculations. 
-In this paper the overlap of an area is artificially reduced and digital elevation models have been created with different image overlaps.
-The DEM's are compared to see how reducing the image overlap influences the result. 
+In this paper the overlap of an area is artificially reduced.
+The image count does have a positive influence on the sparse cloud, but no influence on the points in the dense cloud.
+The DEM's are compared to see how reducing the image overlap influences the DEM result. 
 When the absolute values of the DEM are compared large differences are visible.
@@
 The data covers an area in Ghana, about 20km south east of Ejura (lat. 7.3064212, lon. -1.164493). 
-The area of interest is about 25000 m\textsuperscript{2} and consists mostly of savanna area.
+The area of interest is about 25000 m\textsuperscript{2} and consists of savanna area.
 There are a few trees present on the observed location.
@@
 First, the complete data set has been aligned on medium quality.
-On medium alignment quality the original images are scaled to have 1/2 of the original size.
-%ADD MANUAL
+On medium alignment quality the original images are scaled to have 1/2 of the original size \citep{manual}.
 Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.
-With medium settings the original photo is scaled to 1/4 before used in the dense cloud generation process.
-%ADD MANUAL
+With medium settings the original photo is scaled to 1/4 before used in the dense cloud generation process \citep{manual}.
 A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
-finally after the mesh, the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
+Finally after the mesh, the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
 Because the final product of the photogrammetry process in this paper is a DEM a 2.5D height field was used when the mesh was generated
@@
 The scaling was be done by subtracting the mean and dividing by the standard deviation.
-For further comparison all of the DEM's were be subtracted from the full model DEM.
-%%% CHECK THIS
+The scaled DEM's will be subtracted from the scaled full image count DEM.
 These data will be used to inspect the differences between the scaled DEM of the full image dataset compared to the other DEM's.
@@
 \section{Results}
-In table \ref{tab:ImageProcessing} the result of image processing for each Reduce Overlap settings can be found. 
-The dense clouds contain about the same amount of points with the exception for the lowest Reduce Overlap setting, This setting has resulted in the dense cloud with the most points.
+In table \ref{tab:ImageProcessing} the results of the Reduce Overlap settings for the three different settings can be found. 
+This figure also contains the image processing results for the newly created datasets.
+The lower the Reduce Overlap setting, the less images are left in a dataset, the less points are generated in the sparse cloud.
+The dense clouds contain about the same amount of points with the exception for the lowest Reduce Overlap setting.
+The image set with the lowest image count has resulted in the dense cloud with the most points.
 
@@
     \centering
-    \caption{Image Processing Results}
+    \caption{Reduce Overlap and Image Processing Results}
     \begin{tabular}{@{}cccc@{}}
@@
     \textbf{\begin{tabular}[c]{@{}c@{}}Image\\ Count\end{tabular}} &
-    \textbf{Sparse  Cloud} &
-    \textbf{Dense Cloud} \\ \midrule
+    \textbf{\begin{tabular}[c]{@{}c@{}}Sparse Cloud\\ Points\end{tabular}} &
+    \textbf{\begin{tabular}[c]{@{}c@{}}Dense Cloud\\ Points\end{tabular}} \\ \midrule
     -      & 111 & 80,901 & 3,269,264 \\
@@
     High   & 75  & 49,692 & 3,276,832 \\ \bottomrule
-    % Add processing time!
     \label{tab:ImageProcessing}
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=8.5cm]{DemPlots.png}
+    \includegraphics[width=7cm]{DEM2x2.png}
     \caption{DEM Results of the Reduce Overlap}
@@
     \centering
-    \includegraphics[width=8cm]{DemPlots_scaled.png}
+    \includegraphics[width=7cm]{DEM2x2_scaled.png}
     \caption{Scaled DEM Results of the Reduce Overlap}
@@
     \label{fig:ViolinPlot}
+\end{figure}
+
+In figure \ref{fig:ScaledDifference} the place of the values from the violin plot can be found.
+In this figure it is visible that the difference seems to be lower when the image count increases.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=8cm]{ScaledDemSubstraction.png}
+    \caption{The difference between the original DEM and the scaled DEM's from the reduced image datasets)}
+    \label{fig:ScaledDifference}
 \end{figure}

### 2021-05-02 Paper.tex
20210501 backup

@@
 \section{Introduction}\label{Introduction}
-
 Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
@@
 The process uses similar points visible on multiple images to determine the points in 3D space.
+This will result in a dense cloud containing point with X, Y, Z values.
 The reconstruction certainty of these points is strongly dependent on the overlap between different images.
-A digital elevation model (DEM) is a popular product from photogrammetry \citep{DemIncrease1}.
+The dense cloud can be used to create a digital elevation model (DEM).
+A DEM is a popular product from photogrammetry \citep{DemIncrease1}.
 A DEM is a 2D grid containing height values and is frequently used in geoinformation applications.
 It is therefore important to create high quality DEM's.
+The quality of the DEM relies on the previous step in the photogrammetry process, the dense cloud.
 
@@
 A high overlap is needed in complex structures like vegetation; if parts of the object are not visible on the image, they will not be reconstructed in the point cloud \citep{AccessingImageOverlap}.
-However, an image dataset with a high overlap takes longer to gather, and may require multiple drone flights for a single dataset \citep{uavpop}.
+However, an image dataset with a high overlap takes longer to gather, and may require multiple drone flights for a single dataset \citep{rosnell2012point}.
+
 In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
@@
 %The goal of this study is to investigate the results on the image processing results of using reduced image sets of the same area. 
-This main goal of this study is to investigate how different image overlap influences the DEM result that is created with photogrammetry.
-It will be investigated how the different image overlap influence the intermediate photogrammetry results and processing time.
+The main goal of this study is to investigate how different image overlap of the same area influence the photogrammetry results, and especially the DEM result.
+The processing time of each step will be recorded and a comparison between the full DEM and the DEM's from the reduced image overlap datasets will be made.
 
@@
     \centering
-    \includegraphics[width=7cm]{DEM2x2.png}
+    \includegraphics[width=7.5cm]{DEM2x2.png}
     \caption{DEM Results of the Reduce Overlap}
@@
 There is almost no visual difference visible in the figure, the DEM's look quite similar.
-This is confirmed in figure \ref{fig:BoxPlot_scaled}, only now the boxplot contain the scaled data values.
-These difference seem to be minimal in the scaled boxplots.
 
@@
     \centering
-    \includegraphics[width=7cm]{DEM2x2_scaled.png}
+    \includegraphics[width=7.5cm]{DEM2x2_scaled.png}
     \caption{Scaled DEM Results of the Reduce Overlap}
@@
 
-\begin{figure}[h]
+This is confirmed in figure \ref{fig:BoxPlot_scaled}, only now the boxplot contain the scaled data values.
+These difference seem to be minimal in the scaled boxplots.
+
+\begin{figure}[ht]
     \centering
@@
 In figure \ref{fig:ScaledDifference} the place of the values from the violin plot can be found.
-In this figure it is visible that the difference seems to be lower when the image count increases.
+In this figure it is visible that the difference seems to be less when the image count increases.
 
@@
     \centering
-    \includegraphics[width=8cm]{ScaledDemSubstraction.png}
-    \caption{The difference between the original DEM and the scaled DEM's from the reduced image datasets)}
+    \includegraphics[width=8cm]{ScaledDif_EqualBins.png}
+    \caption{The difference between the original DEM and the scaled DEM's from the reduced image datasets}
     \label{fig:ScaledDifference}
@@
 \section{Discussion}
-The goal of this research was to assess the difference between DEM's of the same area with different image overlap. 
+The goal of this research was to see how a different image overlap of the same areas influences the different steps in the photogrammetry pipeline and especially the DEM result.
+The processing time is also investigated.
 The image reduction in the paper was calculated in Agisoft Metashape with the Reduce Overlap function.
-The amount of images used in the processing does not seem to influence the density of the dense cloud, which was also concluded by \citet{EffectofUABimgcamover}.
-In this research the point confidence was not measured, the dense cloud were directly used to construct a DEM.
 
-%The input mesh for the Reduce Overlap was a 2.5D height field. 
-%This could be of influence, because the 2.5D mesh only takes one single height value into account for each %X, Y combination.
-
-%With more complex objects that need to processed as a real 3D object the quality of dense cloud may decrease if the amount of images is reduces significantly.
-%Because the mesh was structured as a 2.5D surface, difficult points were removed from the model, e.g.
-in this case the tree canopies were constructed, but e.g.
-lower branches were lost in the construction process.
-%An other option is that the Reduce Overlap function will not have much influence on the image count.
+The processing time and the alignment of the images are dependent on the image count.
+Less images result in less computation time, but also less points in the sparse cloud.
+The amount of images used in the processing does not seem to influence the density of the dense cloud, which was also concluded by \citet{EffectofUABimgcamover} 
+The only exception was building the dense cloud for the image data set with the lowest count. 
+%NOG IETS OVER SCHRIJVEN
+However, the image count does influence the time needed to generate the dense cloud; more images means more time needed.
+There is no time difference in the generation of DEM, this is also not a computationally expensive step.
 
@@
 The largest errors differences (around -5/5) between the scaled DEM seem to be the same for all the image datasets.
-The modelling software probably has difficulties in modelling the complex structures of the vegetation, resulting in a larger difference when the image count is lower.
+This is confirmed by looking at the difference between the scaled DEM's in \ref{fig:ScaledDifference}.
+The modelling software seems to have difficulties in modelling the complex structures of the vegetation with a lower image count, resulting in a larger difference when the image count is lower.
 This could result in more error around vegetation canopies where the algorithm has difficulties in accurately measuring the height. 
 \citet{AccessingImageOverlap} also concluded that for complex structures a higher image overlap provides better results. 
+However, in this research this is only visibly assessed as the vegetation locations have not been extracted from the full image dataset.
 An other option may changing the filtering setting provided by the Metashape dense cloud generation.
@@
 \section{Conclusion}
-Using different image overlap in the same area results in DEM's with different absolute values.
+The image overlap does influence the processing time in the photogrammetry process.
+Using different image overlap of the same area results in DEM's with different absolute values.
 The two image dataset with the least images show the largest difference in absolute value range compared to the original dataset with all images. 

### 2021-05-02 Paper.tex
Updates from Overleaf

@@
 The DEM of the dataset with the highest images count seems to be the most similar to the DEM of the full dataset.
+The differences between the DEM's seem to occur around vegetation.
 }
@@
 \citet{AccessingImageOverlap} also concluded that for complex structures a higher image overlap provides better results.
-However, in this research this is only visibly assessed as the vegetation locations have not been extracted from the full image dataset.
+However, in this research this is only visibly assessed as no ground truth vegetation locations have not been extracted from the full image dataset.
+
 An other option may changing the filtering setting provided by the Metashape dense cloud generation.

### 2021-05-04 Paper.tex
20210504 backup

--- 2021-05-02 Paper.tex
@@
 
-\title{Assessing Digital Elevation Models with different image overlap using photogrammetry}
+\title{Assessing differences in the photogrammetry process with different image overlap}
 
 % KAO: Remove extra spacing
-\author{Robert van de Vlasakker\textsuperscript{a}}
+\author{Robert van de Vlasakker\textsuperscript{1}}
 
@@
 \address{
-    \textsuperscript{a}
-    Wageningen University \& Research} % Not needed
+	\textsuperscript{1 }Laboratory of Geo-information Science and Remote
+Sensing, Wageningen University \& Research,\\
+Robert.vandeVlasakker@wur.nl
+}
 
@@
 When the absolute values of the DEM are compared large differences are visible.
-However, when the scaled DEM's are compared in a boxplot the differences appear to be minimal.
-Finally, violin plots have been made of the complete image set DEM minus the reduces image set DEM's.
+However, when the scaled DEM's are compared the differences appear to be minimal.
+Violin plots have been made of the complete image set DEM minus the reduces image set DEM's.
 The more images are used, the more the difference of the DEM's is centered around 0.
 The DEM of the dataset with the highest images count seems to be the most similar to the DEM of the full dataset.
+When plotted the differences between the scaled DEM's seem to occur around vegetation.
 }
@@
 The dense cloud can be used to create a digital elevation model (DEM).
-A DEM is a popular product from photogrammetry \citep{DemIncrease1}.
+A DEM is a popular result from photogrammetry \citep{DemIncrease1}.
 A DEM is a 2D grid containing height values and is frequently used in geoinformation applications.
 It is therefore important to create high quality DEM's.
+
 The quality of the DEM relies on the previous step in the photogrammetry process, the dense cloud.
-
-A higher image overlap results in more similar image points, which will increase the reconstruction certainty of the points \citep{MoreOverMoreAcc}.
+A higher image overlap results in more similar image points, which will increase the reconstruction certainty of the points in the dense cloud \citep{MoreOverMoreAcc}.
 A higher image overlap, does not automatically results in a denser point cloud. \citep{EffectofUABimgcamover}. 
@@
 However, an image dataset with a high overlap takes longer to gather, and may require multiple drone flights for a single dataset \citep{rosnell2012point}.
-
 In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
@@
 The data has been processing on medium settings without any depth filtering for the generation of the dense cloud. 
+In Agisoft Metashape the dense cloud classification algorithm was used to classify the dense cloud in ground points and vegetation points. 
+The vegetation is used as ground truth data for further analysis.
 
@@
     \centering
-    \includegraphics[width=7.5cm]{DEM2x2.png}
+    \includegraphics[width=6.5cm]{DEM2x2.png}
     \caption{DEM Results of the Reduce Overlap}
@@
     \centering
-    \includegraphics[width=8cm]{DemBoxplot.png}
+    \includegraphics[width=7.5cm]{DemBoxplot.png}
     \caption{Box plots of the DEM Results of the Reduce Overlap}
@@
     \centering
-    \includegraphics[width=7.5cm]{DEM2x2_scaled.png}
+    \includegraphics[width=6.5cm]{DEM2x2_scaled.png}
     \caption{Scaled DEM Results of the Reduce Overlap}
@@
 
-\begin{figure}[ht]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=8cm]{DemBoxPlot_Scaled.png}
+    \includegraphics[width=7.5cm]{DemBoxPlot_Scaled.png}
     \caption{Scaled DEM Results of the Reduce Overlap}
@@
     \centering
-    \includegraphics[width=8cm]{ViolinPlotOrdered.png}
+    \includegraphics[width=6.5cm]{ViolinPlotOrdered.png}
     \caption{Violin plot of the difference between the full DEM and the reduced DEM's. All violin plots contain 2.154.300 measurements (1.670 rows x 1.290 columns)}
@@
 
-In figure \ref{fig:ScaledDifference} the place of the values from the violin plot can be found.
-In this figure it is visible that the difference seems to be less when the image count increases.
+In figure \ref{fig:ScaledDifference} the differences of the scaled DEM's have been plotted on top of the ground truth vegetation.
 
-\begin{figure}[h!]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=8cm]{ScaledDif_EqualBins.png}
-    \caption{The difference between the original DEM and the scaled DEM's from the reduced image datasets}
+    \includegraphics[width=7cm]{veg_diff_vert_2.png}
+    \caption{The difference between the original DEM and the scaled DEM's from the reduced image datasets.
+Negative differences are color red and positive differences are color grey.
+The vegetation ground truth data has been plotted with a light green color underneath the differences.}
     \label{fig:ScaledDifference}
@@
 Less images result in less computation time, but also less points in the sparse cloud.
-The amount of images used in the processing does not seem to influence the density of the dense cloud, which was also concluded by \citet{EffectofUABimgcamover} 
+The amount of images used in the processing does not seem to influence the density of the dense cloud, which was also concluded by \citet{EffectofUABimgcamover}. 
 The only exception was building the dense cloud for the image data set with the lowest count. 
-%NOG IETS OVER SCHRIJVEN
+The lowest image count resulted in the dense cloud with the highest point count.
+Because of this, the process time for this dense cloud also took long compared to the other datasets.
+%% WHY
 However, the image count does influence the time needed to generate the dense cloud; more images means more time needed.
-There is no time difference in the generation of DEM, this is also not a computationally expensive step.
+There is no time difference in the generation of DEM, this is not a computationally expensive step and therefore no differences can be detected.
 
@@
 The modelling software seems to have difficulties in modelling the complex structures of the vegetation with a lower image count, resulting in a larger difference when the image count is lower.
-This could result in more error around vegetation canopies where the algorithm has difficulties in accurately measuring the height. 
+
+This is indeed visually confirmed in figure \ref{fig:ScaledDifference}. 
+Larger error are visible around the vegetation when the image overlap decreases.
 \citet{AccessingImageOverlap} also concluded that for complex structures a higher image overlap provides better results.
-However, in this research this is only visibly assessed as the vegetation locations have not been extracted from the full image dataset.
 An other option may changing the filtering setting provided by the Metashape dense cloud generation.
 In this research no depth filtering was used, by applying a more aggressive filtering technique the complex structures of the vegetation will be lost in the DEM generation \citep{AgisoftMetashape}.
-Further research is needed to see where this differences exactly occur and if a different depth filtering may result in different results.
 
 \section{Conclusion}
-The image overlap does influence the processing time in the photogrammetry process.
+The image overlap does influence the processing time in the photogrammetry process, more images means more processing time.
 Using different image overlap of the same area results in DEM's with different absolute values.
@@
 When the scaled values are compared there seems to be a minimal difference between the DEM's.
-If more images are used in the dataset, the difference between the scaled DEM's compared to the full images set becomes smaller; the DEM differences are more centered around 0.
+If more images are used in the dataset, the difference between the scaled DEM's compared to the full images set becomes smaller.
+The differences all seem to occur around the vegetation.
 

### 2021-05-04 Paper.tex
Backup

@@
     \centering
-    \includegraphics[width=7cm]{veg_diff_vert_2.png}
+    \includegraphics[width=7cm]{finalvegplot.png}
     \caption{The difference between the original DEM and the scaled DEM's from the reduced image datasets.
 Negative differences are color red and positive differences are color grey.
-The vegetation ground truth data has been plotted with a light green color underneath the differences.}
+The vegetation ground truth data has been plotted in the right bottom and with a light green color underneath the differences.}
     \label{fig:ScaledDifference}
@@
 \end{document}
-
-Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
-The process uses similar points visible on multiple images to determine the points in 3D space.
-The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
-When a point is visible on more images, the reconstruction certainty will be higher \citep{MoreOverMoreAcc}.
-This is especially the case with the reconstruction of irregular formed object like vegetation \citep{AccessingImageOverlap}.
-With irregular objects, a higher overlap is preferred to capture each side of the object.
-If parts of the object are not visible on the image, they will not be reconstructed in the point cloud.
-In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
-However, a higher image overlap, does not automatically results in a denser point cloud. \citep{EffectofUABimgcamover}. 
-These days most photogrammetry data is acquired with Unmanned Aerial Vehicles (UAV) \citet{UAVAreMoreUsed}. 
-UAV's come with high resolution cameras, GNSS and are available almost anywhere these days.
-While UAV's do come with high resolution sensors and are relatively cheap, small, high capacity batteries are not available \citep{UAVpopularity}.
-A high image overlap takes longer to gather than a low image overlap. 
-A drone can use a higher altitude so the sensor captures a larger area.
-however, with a higher flight altitude the detail of the image will be less than that of a drone with a lower flight altitude.
-This way the gathering process takes longer, and the UAV might even need to switch batteries instead of taking the images in a single flight.
-By reducing the image overlap, time and computing power may be saved without loosing too much spatial information.
-This main goal of this study is to investigate how different image overlap influence the DEM result that is created with photogrammetry.

### 2021-05-07 Paper.tex
Final backup

@@
 
-\title{Assessing differences in the photogrammetry process with different image overlap}
+\title{Assessing photogrammetry results with different image overlap}
 
@@
 \address{
-	\textsuperscript{1 }Laboratory of Geo-information Science and Remote
+	\textsuperscript{1}Laboratory of Geo-information Science and Remote
 Sensing, Wageningen University \& Research,\\
@@
 \abstract{
-Photogrammetry is easy to use these days and can be used to create a digital elevation models (DEM) of an area. 
+Photogrammetry is easy to use these days and is frequently used to create a digital elevation model (DEM) of an area as final output. 
 Image overlap plays an important role in the process of photogrammetry.
-A high overlap takes more time to gather in the field and takes longer to process.
-Less overlap usually results in a less accurate calculations. 
-In this paper the overlap of an area is artificially reduced.
+A high overlap takes more time in the field and the data take longer to process.
+Less overlap usually results in less accurate calculations. 
+In this paper, the overlap of an area is artificially reduced.
 The image count does have a positive influence on the sparse cloud, but no influence on the points in the dense cloud.
-The DEM's are compared to see how reducing the image overlap influences the DEM result. 
-When the absolute values of the DEM are compared large differences are visible.
-However, when the scaled DEM's are compared the differences appear to be minimal.
-Violin plots have been made of the complete image set DEM minus the reduces image set DEM's.
-The more images are used, the more the difference of the DEM's is centered around 0.
-The DEM of the dataset with the highest images count seems to be the most similar to the DEM of the full dataset.
-When plotted the differences between the scaled DEM's seem to occur around vegetation.
+The DEMs are compared to see how reducing the image overlap influences the DEM result. 
+When the absolute values of the DEM are compared, large differences are visible.
+However, when the scaled DEMs are compared the differences appear to be minimal.
+Differences between the scaled DEMs how that the more images are used, the more the difference of the DEMs is centered around 0.
+The DEM of the dataset with the highest image count seems to be the most similar to the DEM of the full dataset.
+When plotted, the differences between the scaled DEMs seem to occur around vegetation.
 }
 
-\keywords{Photogrammetry, Digital Elevation Model, Image Overlap, Agisoft Metashape}
+\keywords{Photogrammetry, Digital Elevation Model, Image Overlap, Dense Cloud, Agisoft Metashape}
 
 \maketitle
-
-%\saythanks % added 28-02-2014 Markus Englich
 
@@
 These days most photogrammetry data is acquired with unmanned aerial vehicles (UAV) \citep{UAVAreMoreUsed}. 
-UAV's come with GNSS and provide high resolution images needed for photogrammetry.
+UAVs come with GNSS and provide high-resolution images needed for photogrammetry.
 The process uses similar points visible on multiple images to determine the points in 3D space.
-This will result in a dense cloud containing point with X, Y, Z values.
+This will result in a dense cloud containing points with X, Y, Z values.
 The reconstruction certainty of these points is strongly dependent on the overlap between different images.
-The dense cloud can be used to create a digital elevation model (DEM).
+Finally, the dense cloud can be used to create a digital elevation model (DEM).
 A DEM is a popular result from photogrammetry \citep{DemIncrease1}.
 A DEM is a 2D grid containing height values and is frequently used in geoinformation applications.
-It is therefore important to create high quality DEM's.
+It is therefore important to create high-quality DEMs.
 
@@
 A higher image overlap results in more similar image points, which will increase the reconstruction certainty of the points in the dense cloud \citep{MoreOverMoreAcc}.
-A higher image overlap, does not automatically results in a denser point cloud. \citep{EffectofUABimgcamover}. 
+A higher image overlap does not automatically result in a denser point cloud. \citep{EffectofUABimgcamover}. 
 A high overlap is needed in complex structures like vegetation; if parts of the object are not visible on the image, they will not be reconstructed in the point cloud \citep{AccessingImageOverlap}.
@@
 In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
-By reducing the image overlap, time and computing power may be saved without loosing too much spatial information.
-%The goal of this study is to investigate the results on the image processing results of using reduced image sets of the same area. 
-The main goal of this study is to investigate how different image overlap of the same area influence the photogrammetry results, and especially the DEM result.
-The processing time of each step will be recorded and a comparison between the full DEM and the DEM's from the reduced image overlap datasets will be made.
+By reducing the image overlap, time and computing power may be saved without losing too much spatial information.
+The main goal of this study is to investigate how different image overlaps of the same area influence the photogrammetry results, and especially the DEM result.
+The processing time of each step will be recorded and a comparison between the full DEM and the DEMs from the reduced image overlap datasets will be made.
 
@@
 \subsection{Study Area}\label{sec:Study Area}
-The data covers an area in Ghana, about 20km south east of Ejura (lat. 7.3064212, lon. -1.164493). 
+The data covers an area in Ghana, about 20km south-east of Ejura (lat. 7.3064212, lon. -1.164493). 
 The area of interest is about 25000 m\textsuperscript{2} and consists of savanna area.
-There are a few trees present on the observed location.
-Each image has a resolution of 4000 times 3000 and was taken by a DJI Phantom 3.
+There are a few trees present in the observed location.
+Each image has a resolution of 4000 times 3000 pixels and was taken by a DJI Phantom 3.
 The images all contain a GNNS location (WGS84). 
@@
     \includegraphics[width=4cm]{imgloc.png}
-    \caption{Area of Interest and Unprocessed Image GPS Locations}
+    \caption{Area of interest and unprocessed image GPS locations}
     \label{fig:areaofinterest}
@@
 First, the complete data set has been aligned on medium quality.
-On medium alignment quality the original images are scaled to have 1/2 of the original size \citep{manual}.
+On medium alignment quality, the original images are scaled to have 1/2 of the original size \citep{manual}.
 Next, the dense cloud was built on medium quality (no depth filtering), resulting in a dense cloud of 3,268,264 points.
-With medium settings the original photo is scaled to 1/4 before used in the dense cloud generation process \citep{manual}.
-A mesh was built using the the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
-Finally after the mesh, the Reduce Overlap function was used to reduce the amount images used in the process of photogrammetry. 
-Because the final product of the photogrammetry process in this paper is a DEM a 2.5D height field was used when the mesh was generated
+With medium settings, the original photo is scaled to 1/4 before used in the dense cloud generation process \citep{manual}.
+A mesh was built using the triangulated irregular network (TIN) algorithm by \citet{axelsson1999processing}. 
+Finally, after the mesh, the Reduce Overlap function was used to reduce the number of images used in the process of photogrammetry. 
+Because the final product of the photogrammetry process in this paper is a DEM, a 2.5D height field was used when the mesh was generated.
 The 2.5D height field mesh contains only one Z value for any X, Y coordinate combination, this is also the case in the final DEM.
@@
 The algorithm of the Reduce Overlap function tries to select a minimal amount of images such that each point of the model is observed from N locations/angles.
-If a point is observed multiple times from the same location/angle, than this still counts as one. 
-As in this research a height field was used, the algorithm will probably take the vegetation canopy into account in the reconstruction, but lower branches may be lost in the process.
+If a point is observed multiple times from the same location/angle then this still counts as one observation. 
+In this research a height field was used, the algorithm will take the vegetation canopy into account in the reconstruction, but lower branches may be lost in the process.
 This will have some influence on the Reduce Overlap setting; it becomes more flexible because single height values are used for each X, Y coordinate combination.
 The algorithm and parameters behind the Agisoft Reduce Overlap function are proprietary software and therefore unfortunately unknown.
-In Agisoft Metashape the Reduce Overlap had three different settings, low, medium and high. 
+In Agisoft Metashape the Reduce Overlap had three different settings: low, medium and high. 
 All of the settings are used and the remaining images are used for further processing.
 The images are matched based on an adapted version of the SIFT algorithm \citep{lowe1999object, AgisoftMetashape}.
-All the datasets are processed on medium settings for the image alignment.
+All the datasets are processed on medium settings for image alignment.
 
 \textbf{Dense Cloud.}
-The result of the alignment of the images is used as input for the dense cloud generation.
-The data has been processing on medium settings without any depth filtering for the generation of the dense cloud. 
+The alignment result of the images was used as input for the dense cloud generation.
+The data were processed on medium settings without any depth filtering for the generation of the dense cloud. 
 In Agisoft Metashape the dense cloud classification algorithm was used to classify the dense cloud in ground points and vegetation points. 
-The vegetation is used as ground truth data for further analysis.
+The vegetation was used as ground truth data for further analysis.
 
 \textbf{DEM.}
-The source data for the DEM's are the dense cloud results. 
-The TIN algorithm is used to built the DEM's \citep{axelsson1999processing}.
-Because the dense clouds are unique the TIN algorithm also results in four unique DEM's.
-These DEM's all have a slightly different extent and resolution.
-For further comparison the DEM's have all been cropped on the largest common extent and the pixel resolution was set to 17.5 cm per pixel (1670 x 1290 pixels).
-The DEM's were also be scaled to check the differences between the DEM's without looking at the absolute values.
-The scaling was be done by subtracting the mean and dividing by the standard deviation.
-The scaled DEM's will be subtracted from the scaled full image count DEM.
-These data will be used to inspect the differences between the scaled DEM of the full image dataset compared to the other DEM's.
+The source data for the DEMs are the dense cloud results. 
+The TIN algorithm was applied to build the DEMs \citep{axelsson1999processing}.
+Because the dense clouds are unique, the TIN algorithm also results in four unique DEMs.
+For further comparison, the DEMs have all been cropped on the largest common extent and the pixel resolution was set to 17.5 cm per pixel (1670 x 1290 pixels).
+The DEMs were also scaled to check the differences between them without looking at the absolute values.
+The scaling was done by subtracting the mean and dividing it by the standard deviation.
+The scaled DEMs were subtracted from the scaled DEM that was created with all images.
+This data was used to inspect the differences between the scaled DEM of the full image dataset compared to the other DEMs.
 
 \section{Results}
-In table \ref{tab:ImageProcessing} the results of the Reduce Overlap settings for the three different settings can be found. 
-This figure also contains the image processing results for the newly created datasets.
-The lower the Reduce Overlap setting, the less images are left in a dataset, the less points are generated in the sparse cloud.
-The dense clouds contain about the same amount of points with the exception for the lowest Reduce Overlap setting.
+In table \ref{tab:ImageProcessing} the image processing results can be found. 
+It also contains the image processing results for the newly created datasets.
+The lower the Reduce Overlap setting, the fewer images are left in a dataset and the fewer points are generated in the sparse cloud.
+The dense clouds contain about the same amount of points except for the lowest Reduce Overlap setting.
 The image set with the lowest image count has resulted in the dense cloud with the most points.
@@
 
-After all the new datasets with the images have been aligned the camera locations are estimated, in figure \ref{fig:cameralocation} camera locations can be found. 
+After all the new datasets with the images have been aligned, the camera locations are estimated.
+In figure \ref{fig:cameralocation} camera locations can be found. 
 None of the images used in the alignment process failed to align.
@@
 
-In figure \ref{fig:DemPlot_unscaled} the DEM's are visualized using the same color range. 
-In this figure the DEM's do no look similar at all.
+In figure \ref{fig:DemPlot_unscaled} the DEMs are visualized using the same colour range. 
+The DEMs are distinguishable.
 
@@
 
-As can be seen from figure \ref{fig:BoxPlot_unscaled} the DEM's are indeed different from each other. 
-For the low setting the DEM values range from -19.4 to 19.0, for the medium setting the values range from -22.7 to 16.2, for the high setting the values range from 13.1 to 20.0 and for the full model from -4.8 to 28.9.
+The boxplots in Figure \ref{fig:BoxPlot_unscaled} confirm this observation. 
+For the low setting, the DEM values range from -19.4 to 19.0, for the medium setting the values range from -22.7 to 16.2, for the high setting the values range from 13.1 to 20.0 and for the full model from -4.8 to 28.9.
+Units are in meters.
 
@@
     \includegraphics[width=7.5cm]{DemBoxplot.png}
-    \caption{Box plots of the DEM Results of the Reduce Overlap}
+    \caption{Box plots of the DEM results of the Reduce Overlap}
     \label{fig:BoxPlot_unscaled}
@@
 
-Figure \ref{fig:DemPlot_scaled} contains the same visualization of DEM plots, only for all the DEM's the data has been scaled.
-There is almost no visual difference visible in the figure, the DEM's look quite similar.
+Figure \ref{fig:DemPlot_scaled} contains the same visualization of DEM plots, only for all the DEMs, the data has been scaled.
+The DEMs look similar in this figure.
 
@@
 This is confirmed in figure \ref{fig:BoxPlot_scaled}, only now the boxplot contain the scaled data values.
-These difference seem to be minimal in the scaled boxplots.
+The differences seem to be minimal in the scaled boxplots.
 
@@
 
-Figure \ref{fig:ViolinPlot} contains three violin plots. For each of the plots the scaled DEM's from the reduced image datasets has been subtracted from the scaled full dataset DEM.
-It is visible that the overall scaled error difference of the scaled DEM's varies from around -5.0 to 5.0.
+Figure \ref{fig:ViolinPlot} contains three violin plots. 
+For each of the plots, the scaled DEMs from the reduced image datasets has been subtracted from the scaled full dataset DEM.
+It is visible that the overall scaled error difference of the scaled DEMs varies from around -5.0 to 5.0.
 For the high settings, the differences are more centered around zero, while this is not the case for low and medium settings.
-For medium setting the difference is slightly more centered around 0.0 than low settings.
+For the medium setting, the difference is slightly more centered around 0.0 than in the low setting.
 
@@
     \includegraphics[width=6.5cm]{ViolinPlotOrdered.png}
-    \caption{Violin plot of the difference between the full DEM and the reduced DEM's. All violin plots contain 2.154.300 measurements (1.670 rows x 1.290 columns)}
+    \caption{Violin plot of the difference between the full DEM and the reduced DEMs. All violin plots contain 2.154.300 measurements (1.670 rows x 1.290 columns)}
     \label{fig:ViolinPlot}
@@
 
-In figure \ref{fig:ScaledDifference} the differences of the scaled DEM's have been plotted on top of the ground truth vegetation.
+In figure \ref{fig:ScaledDifference} the differences of the scaled DEMs have been plotted on top of the ground truth vegetation.
 
@@
     \includegraphics[width=7cm]{finalvegplot.png}
-    \caption{The difference between the original DEM and the scaled DEM's from the reduced image datasets.
-Negative differences are color red and positive differences are color grey.
-The vegetation ground truth data has been plotted in the right bottom and with a light green color underneath the differences.}
+    \caption{The difference between the original DEM and the scaled DEMs from the reduced image datasets.
+Negative differences are red and positive differences are grey.
+The vegetation ground truth data has been plotted in the right bottom with a light green color and underneath the differences.}
     \label{fig:ScaledDifference}
@@
 The processing time is also investigated.
-The image reduction in the paper was calculated in Agisoft Metashape with the Reduce Overlap function.
+The image reduction in the paper was done in Agisoft Metashape with the Reduce Overlap function.
 
 The processing time and the alignment of the images are dependent on the image count.
-Less images result in less computation time, but also less points in the sparse cloud.
+Fewer images result in less computation time, but also fewer points in the sparse cloud.
 The amount of images used in the processing does not seem to influence the density of the dense cloud, which was also concluded by \citet{EffectofUABimgcamover}. 
@@
 The lowest image count resulted in the dense cloud with the highest point count.
-Because of this, the process time for this dense cloud also took long compared to the other datasets.
-%% WHY
+Because of this, the processing time for this dense cloud was higher compared to the other datasets.
 However, the image count does influence the time needed to generate the dense cloud; more images means more time needed.
-There is no time difference in the generation of DEM, this is not a computationally expensive step and therefore no differences can be detected.
+There is no time difference in the generation of the DEMs.
+It is not a computationally expensive step and therefore no differences can be detected.
 
-There is a large different between the absolute values between the different DEM's, this can be seen visually in figure \ref{fig:DemPlot_unscaled} and also when comparing the boxplot values in figure \ref{fig:BoxPlot_unscaled}.
+There is a large difference between the absolute values of the different DEMs, this can be seen visually in figure \ref{fig:DemPlot_unscaled} and also when comparing the boxplot values in figure \ref{fig:BoxPlot_unscaled}.
 The outliers in both boxplot figures are probably the vegetation that is present in the area as the boxplots only contain high outliers.
-With the use of at least three ground control points the error in the absolute values of the can be reduced \citep{AssessingUAVGCPS, GCPbetterAccuracy, GeoreferencedPointClouds}.
-Using GCP's in the different image dataset will reduce the absolute error.
+With the use of at least three ground control points, the error in the dense cloud will be reduced \citep{AssessingUAVGCPS, GCPbetterAccuracy, GeoreferencedPointClouds}.
+As the relative points in all of the DEMs do not differ, using ground control points can correct the absolute error value.
+In the end, this will result in a dense cloud with a higher point accuracy and fewer errors in the absolute values of the DEM.
 
-The violin plots indicate that the dataset with the highest image count is most similar to the full dataset; the difference of is more centered around zero, while the two lower image count datasets are more widespread.
+The violin plots indicate that the dataset with the highest image count is most similar to the full dataset. 
+The difference of the scaled DEMs is more centered around zero, while the two lower image count datasets are more widespread.
 The largest errors differences (around -5/5) between the scaled DEM seem to be the same for all the image datasets.
-This is confirmed by looking at the difference between the scaled DEM's in \ref{fig:ScaledDifference}.
-The modelling software seems to have difficulties in modelling the complex structures of the vegetation with a lower image count, resulting in a larger difference when the image count is lower.
-
-This is indeed visually confirmed in figure \ref{fig:ScaledDifference}. 
-Larger error are visible around the vegetation when the image overlap decreases.
-\citet{AccessingImageOverlap} also concluded that for complex structures a higher image overlap provides better results.
-An other option may changing the filtering setting provided by the Metashape dense cloud generation.
-In this research no depth filtering was used, by applying a more aggressive filtering technique the complex structures of the vegetation will be lost in the DEM generation \citep{AgisoftMetashape}.
+This is confirmed by looking at the difference between the scaled DEMs in \ref{fig:ScaledDifference}.
+Agisoft Metashape seems to have difficulties in modelling the complex structures of the vegetation with less image overlap, which is visually confirmed in figure \ref{fig:ScaledDifference}. 
+In this figure larger errors are visible around the vegetation.
+\citet{AccessingImageOverlap} also concluded that a high image overlap is needed to model complex structures.
+Another option could be changing the filtering setting provided by the Metashape dense cloud generation.
+In this research, no depth filtering was used.
+By applying a more aggressive filtering algorithm the complex structures of the vegetation will be lost in the DEM generation and therefore will not appear as errors anymore in the comparison \citep{AgisoftMetashape}.
+If the final product from the photogrammetry pipeline is a DEM, a lower image overlap can be used as most of the differences compared to the full image dataset appear around the vegetation and not in the ground elevation.
 
 \section{Conclusion}
-The image overlap does influence the processing time in the photogrammetry process, more images means more processing time.
-Using different image overlap of the same area results in DEM's with different absolute values.
-The two image dataset with the least images show the largest difference in absolute value range compared to the original dataset with all images.
-The image dataset with the highest image count, has a DEM that is most similar compared to the original dataset.
-When the scaled values are compared there seems to be a minimal difference between the DEM's.
-If more images are used in the dataset, the difference between the scaled DEM's compared to the full images set becomes smaller.
+The image overlap does influence the processing time in the photogrammetry process. 
+More images mean more processing time.
+Using different image overlap of the same area results in DEMs with different absolute values.
+The two image datasets with the least images show the largest difference in absolute value range compared to the original dataset with all images.
+The image dataset with the highest image count has a DEM that is most similar compared to the original dataset.
+When the scaled values are compared, there seems to be a minimal difference between the DEMs.
+If more images are used in the dataset, the difference between the scaled DEMs becomes smaller.
 The differences all seem to occur around the vegetation.
